### 2020-05-04 tex/report.tex
Added report files

\documentclass[twocolumn,showpacs,%
  nofootinbib,aps,superscriptaddress,%
  eqsecnum,prd,notitlepage,showkeys,10pt]{revtex4-1}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{float}

% 14 Jan 2020: Reduce spacing around sections
% https://tex.stackexchange.com/questions/101116/how-to-reduce-the-space-before-after-section-and-subsection
\usepackage{titlesec}
\titlespacing*{\section}{\baselineskip}{1.4\baselineskip}{\baselineskip}
\titlespacing*{\subsection}{\baselineskip}{\baselineskip}{0.7\baselineskip}

\begin{document}

\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}
% \renewcommand{\topfraction}{.86}
% \renewcommand{\bottomfraction}{.71}
% \renewcommand{\textfraction}{.14}
% \renewcommand{\floatpagefraction}{.68}
% \renewcommand{\dbltopfraction}{.68}
% \renewcommand{\dblfloatpagefraction}{.68}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}

\title{Fine-grained Image Outpainting}
\author{Przemek Gardias \qquad
Eric Arthur \qquad
Huaming Sun \\ [0.1cm]
\textit{Worcester Polytechnic Institute} \\ [0.05cm]
\texttt{\{etarthur, pmgardias, hsun2\}@wpi.edu} \\ [0.05cm]
}
% \affiliation{Worcester Polytechnic Institute}

\begin{abstract}
\textbf{Abstract} \hspace{0.3cm}
"And, But, Therefore":
Although the task of predicting the content of an image outside of the existing bounds has been explored in few cases...

Although the inherently ambiguous task of predicting what resides beyond all four edges of an image has rarely been explored before, we demonstrate that GANs hold powerful potential in producing reasonable extrapolations. Two outpainting methods are proposed that aim to instigate this line of research: the first approach uses a context encoder inspired by common inpainting architectures and paradigms, while the second approach adds an extra post-processing step using a single-image generative model. This way, the hallucinated details are integrated with the style of the original image, in an attempt to further boost the quality of the result and possibly allow for arbitrary output resolutions to be supported.
\end{abstract}

\maketitle

\begin{figure}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\columnwidth]{GenIdea3}
  \end{adjustbox}
  \caption{Image outpainting idea.}
  \label{fig:GenIdea}
\end{figure}

\section{INTRODUCTION}

\hspace{\parindent}

When presented with an incomplete image, humans are excellent at filling in the blanks and producing a realistic explanation for what could be missing. Image inpainting is a well-studied problem that replicates this behaviour, often tasking deep neural networks with trying to understanding the semantic content of natural images in order to recover the missing regions of a photo. However, the spatially inverted variant of this problem is even more challenging and, with a small play on words, can be denoted \textit{outpainting}. The problem statement is shown in Figure \ref{fig:GenIdea}; essentially, the task is to extrapolate the image content rather than to interpolate within an image. More formally, we must design a generator $G$ that converts an image $x$ with dimensions $n*n$ into a larger image $G(x)$ with dimensions $m*m$, such that the center part of $G(x)$ looks the same as $x$, while the complete outpainted image $G(x)$ should be a plausible hypothesis of what could encompass the original image. In particular, the generated parts should look realistic, despite the fact that it is often impossible to know precisely what the scene contains outside of the pictured boundaries. Figure \ref{fig:B3_samples} gives a practical illustration of what is accomplished in this work. Possible applications
of outpainting include the opportunity to experience and explore multimedia more immersively, enabling technologies similar to Ambilight to produce much richer and/or realistic surroundings, or merely as a form of computer-generated art that can be appreciated aesthetically.

\begin{figure}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\columnwidth]{B3_samples}
  \end{adjustbox}
  \caption{Demonstration of the outpainting task, as achieved using an adversarially trained generator.}
  \label{fig:B3_samples}
\end{figure}

\subsection{Related Work}

Deep neural networks have recently shown great performance in image completion. This section discusses previous work related to the proposed methods for outpainting.

\textbf{Self-supervised learning} \hspace{0.3cm}
The automatic generation of a supervision signal, by systematically omitting certain parts of the input data, grants the ability to capitalize on the vast amounts of unlabeled images and videos that are available on the Web. For example, both colorization \cite{Larsson2017} and predicting the relative spatial position of two patches \cite{Doersch2015, Noroozi2016} have been proven to be successful pretext tasks to representation learning. These methods do not require any labellings of the dataset, since the inputs (gray-scale images resp. patches) as well as their corresponding ground truths (color images resp. locations) can be extracted procedurally.

\textbf{Generative Adversarial Networks} \hspace{0.3cm}
Image or video generation using convolutional neural networks with an adversarial loss \cite{Goodfellow2014} has attracted significant research interest. The idea is to let a \textit{generator} network $G$ create samples according to some distribution, and subsequently have an auxiliary network called the \textit{discriminator} $D$ try to distinguish whether a given sample is valid or was actually generated by $G$. These two components are trained in a quick alternation, where $G$ trying to fool $D$ forces $D$ to become better at telling real from fake, which in turn motivates $G$ to synthesize increasingly convincing outputs \cite{Iizuka2017}. From the perspective of game theory, GANs can be viewed as a zero-sum two-player game; as such, they are comparatively hard to train. In fact, it turns out that the conditions for their convergence is still an open research problem \cite{Mescheder2018}.

\textbf{Inpainting and Context Encoders} \hspace{0.3cm}
Recovering holes within images has important applications for the restoration of damaged media, and can be achieved by training GANs in a self-supervised way. Specifically, a generator can learn to 'fill in the blanks' by using an encoder-decoder network that encodes the surrounding context in order to understand the image content, and subsequently produces a plausible hypothesis for the missing square \cite{Pathak2016}. More recent improvements include attempts to complete images of arbitrary resolutions by filling in regions of any shape, and employing two types of discriminators (\textit{global} and \textit{local}) in order to enforce both overall consistency as well as realistic details \cite{Iizuka2017}.

\textbf{Outpainting} \hspace{0.3cm}
The problem opposite to inpainting comprises predicting which pixels reside beyond the borders of a fully intact photo, and has to our knowledge been explored only few times before by the academic research community \cite{Zhang2013, Sabini2018, Wang2019}. One approach geometrically extrapolates the field of view of an image using another panoramic reference image of the same scene category using old-school computer vision techniques \cite{Zhang2013}, while a more recent relevant paper uses a GAN to perform horizontal outpainting \cite{Sabini2018}. Results look promising, although there is room for visual improvement in terms of making the hallucinations omnidirectional and increasing the output resolution. \cite{Wang2019} achieves impressive outcomes but tends to focus on limited domain datasets (such as faces only), and notes that generative models experience difficulties trying to fit datasets as diverse as Places2. Lastly, Google's Snapseed application has a proprietary 'Expand' functionality that seems to select patches from the image and copy them to the edges \cite{snapseed}, but a limited number of experiments suggest that this tool fails to capture the local structure of most scenes from region to region; see Figure \ref{fig:snapseed_fail}.

\begin{figure}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\columnwidth]{snapseed1_fail}
  \end{adjustbox}
  \caption{Demonstrating Snapseed's \cite{snapseed} unrealistic results upon running the 'Expand' feature on a natural photograph.}
  \label{fig:snapseed_fail}
\end{figure}

\textbf{Single-image generative models} \hspace{0.3cm}
The recently introduced SinGAN framework can train an unconditional generative model on a single natural photo, capturing and reproducing image statistics across various scales of the image \cite{Shaham2019}. It allows for the creation of random samples with new object configurations by starting from a low-resolution sample at the coarsest scale, and then progressively upsampling and refining the result through the pyramid of generators. By carefully modifying the initial sample, SinGAN can be used to perform several image manipulation tasks such as editing photos, splicing foreign objects into the scene and subsequently harmonizing their style with the environment, or even superresolution.

\section{METHODS}

\subsection{Datasets}

\hspace{\parindent} During training, we decide to crop images first before feeding them into the generator. Consequently, learning can be done in a self-supervised way thanks to the fact that we are now able to enforce the output to approximate the original, uncropped image. Any sufficiently large dataset of unlabelled, natural photos will therefore suffice. We continue with the MIT CSAIL Places365-Standard dataset, which contains millions of images with landscapes, buildings and other everyday scenarios intended for scene recognition \cite{Zhou2018}. A second set of experiments was performed with a dataset consisting of images scraped from WikiArt \cite{wikiart}. This website holds a database of visual artwork belonging to many different categories.

The photos will first be resized to 192x192 as a preprocessing step, and the generator will then be tasked with expanding a crop of 128x128 back into a 192x192 image. Note that adding 32-pixels at every boundary might not seem significant, but we consider this configuration to be quite ambitious already: the total output size is 2.25 times that of the input, meaning that over half of all pixels will be hallucinated. In practice, the generator $G$ maps a partially masked 192x192 color image to an outpainted variant of the same dimensions, with the masked part replaced by the model's predictions.

\begin{figure*}[tp]
  \centering
  \begin{adjustbox}{center}
  \includegraphics[width=\textwidth]{MyArch}
  \end{adjustbox}
  \caption{Context encoder trained with joint reconstruction and adversarial loss for semantic outpainting, based on \cite{Pathak2016}. Note that as opposed to inpainting, the decoder is almost an exact mirroring of the encoder, since both input and output have the same dimensions.}
  \label{fig:MyArch}
\end{figure*}

\begin{table}[tp]
\centering
\footnotesize
\begin{tabular}{l c c}
  \hline
  Type & Kernel size & $(H,W,C)$ \\ \hline\hline
  Conv + Leaky ReLU & $4 * 4$ & $(96, 96, 64)$ \\
  Conv + BatchNorm + Leaky ReLU & $4 * 4$ & $(48, 48, 64)$ \\
  Conv + BatchNorm + Leaky ReLU & $4 * 4$ & $(24, 24, 128)$ \\
  Conv + BatchNorm + Leaky ReLU & $4 * 4$ & $(12, 12, 256)$ \\
  Conv + BatchNorm + Leaky ReLU & $4 * 4$ & $(6, 6, 512)$ \\
  Conv & $4 * 4$ & $(3, 3, 4000)$ \\
  Up-conv + BatchNorm + ReLU & $4 * 4$ & $(6, 6, 512)$ \\
  Up-conv + BatchNorm + ReLU & $4 * 4$ & $(12, 12, 256)$ \\
  Up-conv + BatchNorm + ReLU & $4 * 4$ & $(24, 24, 128)$ \\
  Up-conv + BatchNorm + ReLU & $4 * 4$ & $(48, 48, 64)$ \\
  Up-conv + BatchNorm + ReLU & $4 * 4$ & $(96, 96, 64)$ \\
  Up-conv + BatchNorm + Tanh & $4 * 4$ & $(192, 192, 3)$ \\ \hline
\end{tabular}
\caption{Layers of the generator network $G$.}
\label{tab:layers_G}
\end{table}

\begin{table}[tp]
\centering
\footnotesize
\begin{tabular}{l c c}
  \hline
  Type & Kernel size & $(H,W,C)$ \\ \hline\hline
  Conv + Leaky ReLU & $3 * 3$ & $(96, 96, 64)$ \\
  Conv + InstanceNorm + Leaky ReLU & $3 * 3$ & $(48, 48, 128)$ \\
  Conv + InstanceNorm + Leaky ReLU & $3 * 3$ & $(24, 24, 256)$ \\
  Conv + InstanceNorm + Leaky ReLU & $3 * 3$ & $(24, 24, 512)$ \\
  Conv & $3 * 3$ & $(24, 24, 1)$ \\ \hline
\end{tabular}
\caption{Layers of the discriminator network $D$.}
\label{tab:layers_D}
\end{table}

\subsection{Architecture}

\hspace{\parindent} Many architectural aspects and ideas can be naturally adopted from inpainting. The context encoder part of the generator network $G$ repeatedly downsamples the masked input through six convolutional layers, in order to efficiently capture the image content and object semantics within some embedding space. Next, the decoder consists of a special kind of layers called \textit{up-convolutional} or \textit{deconvolutional}, which can be understood as having a fractional stride in order to 'undo' the downsampling performed by the encoder \cite{Pathak2016}.

The discriminator $D$ is another deep neural network that estimates the probability of the ground truth or the hallucinated image being real. In inpainting, $D$ typically sees the generated part only \cite{Pathak2016}, although in this project we decide to operate on the full outpainted image in order to discourage $G$ from introducing obvious perceptual discontinuities or other kinds of structural inconsistencies. The architecture we use for $D$ results in a $24*24$ grid of probabilities whose errors are averaged during the training process.

See Figure \ref{fig:MyArch} as well as Tables \ref{tab:layers_G} and \ref{tab:layers_D} for a detailed overview of the system architecture.

\subsection{Training}

\hspace{\parindent} Training is done for 200 epochs, with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$. The loss functions are as follows:
\begin{align}
  L_{rec} &= ||x-G(x)||_1 \\
  L_{adv} &= ||D(G(x))-1||_2^2 \\
  L_G &= \lambda_{rec}L_{rec} + \lambda_{adv}L_{adv} \\
  L_D &= ||D(x)-1||_2^2 + ||D(G(x))-0||_2^2
\end{align}
Using an $L_1$ reconstruction loss instead of $L_2$ helps produce less blurry images \cite{Huang2018}. The weight of the adversarial loss $\lambda_{adv}$ relative to the reconstruction loss $\lambda_{rec}=1-\lambda_{adv}$ turned out to be particularly tricky to adjust; this factor was initially set to $\lambda_{adv}=0.001$ as in various existing works \cite{Pathak2016, Li2018, Sabini2018}, although the GAN kept collapsing into a failure mode where the adversarial loss did not move away from $1$. This means that $G$ was unable to fool $D$, so $D$ was ahead of $G$ and could always tell real from fake successfully. A working remedy involved varying $\lambda_{adv}(n)$ throughout time as a function of the epoch $n$ as follows:
\begin{align}
  \lambda_{adv}(n) = \begin{cases}
    0.001, & \text{if }n\leq10 \\
    0.005, & \text{if }10<n\leq30 \\
    0.015, & \text{if }30<n\leq60 \\
    0.040, & \text{otherwise}
  \end{cases}
  \label{eq:loss_adv}
\end{align}
This will punish the generator more heavily for producing unrealistic outputs as time progresses, rather than just enforcing an accurate pixel-wise reconstruction.

\subsection{Harmonization}

\hspace{\parindent} Due to the visual fuzziness of our initial experiments, we came up with the idea of leveraging SinGAN's harmonization capabilities in an attempt to improve the fidelity of the hallucinated outputs, serving as a second possible approach to the outpainting problem. To this end, we first train a SinGAN model on the original high-quality image, then propagate it forward through the outpainting generator (which produces a low-resolution output), and then try to super-resolve this result by injecting it into one of the coarser scales of SinGAN. The hope is that the model will harmonize the outpainted parts with the style of the original image that it was trained on, while simultaneously synthesizing a finer-scale, higher-resolution variant by pushing it up through the hierarchy of multi-scale generators.\footnote{Note that our definition of the term \textit{harmonization} is slightly different from what is actually meant in the referred paper, but the underlying process is exactly what we intend to perform anyway.}

\begin{figure}[tp]
  \centering
  \begin{subfigure}[b]{\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{hist_B3}
      \caption{Places365 (green line marks restart).}
      \vspace{0.2cm}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{hist_B4}
      \caption{WikiArt.}
  \end{subfigure}
  \caption{Learning curves for the outpainting GAN, where the difficulty of training GANs is observed.}
  \label{fig:learn_curves}
\end{figure}

\section{RESULTS}

\subsection{Experiments}

\hspace{\parindent} Three models were trained and evaluated, differing in the following aspects:
\begin{itemize}
  \item 200k images of Places365, with $L_G = L_{rec}$, so only the $L_1$ reconstruction loss is considered.
  \item 200k images of Places365, with fully functional joint reconstruction and adversarial loss functions.
  \item 50k images of WikiArt, with fully functional joint loss functions.
\end{itemize}
Since training takes a long time, the second model's training process was momentarily interrupted and resumed in order to upgrade the adversarial loss weight to the better performing Equation \ref{eq:loss_adv}. Selected learning curves are plotted in Figure \ref{fig:learn_curves}. Note that the discriminator $D$ seems to have a harder time deciding for the WikiArt dataset than for Places365, both in terms of adversarial loss $L_{adv}$ and regular discriminator loss $L_D$. This suggests a priori that the artwork domain is inherently more diverse than natural scenery in a visual sense, making it harder to reliably classify the authenticity of samples.

\begin{table}[tp]
\centering
\begin{tabular}{l r r}
  \hline
  Model & Mean $MSE(G(x),y)$ & Mean $D(G(x))$ \\ \hline\hline
  Places365 rec & 0.0181 & 0.0791 \\
  Places365 rec + adv & 0.0230 & 0.1705 \\
  WikiArt rec + adv & 0.0227 & 0.2371 \\ \hline
\end{tabular}
\caption{Mean square error and realism (i.e. probability of legitimacy) statistics.}
\label{tab:quant}
\end{table}

\subsection{Evaluations}

\hspace{\parindent} In the final step of the outpainting pipeline, the input is pasted on top of and blended with the output using a simple 16-pixel wide gradient alpha mask. Compression artefacts arising from the autoencoder-like operation at the center of the image are thus resolved by simply hiding them. However, two quantitative performance metrics, the mean squared error and the discriminator's output values, are calculated from the original, unmodified result. See Table \ref{tab:quant} for an overview of these metrics for the three trained models as calculated on the respective test sets. Including the adversarial loss increases the reconstruction loss, and outpainted artwork fools the discriminator more often than when we stay within the domain of natural images.

\begin{figure*}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\textwidth]{B2_B3_cmp3}
  \end{adjustbox}
  \caption{Comparison between outpainting on Places365 without or with adversarial loss, demonstrating blurry results in the former case.}
  \label{fig:B2_B3_cmp}
\end{figure*}

\textbf{Non-adversarial versus adversarial models} \hspace{0.3cm}
See Figure \ref{fig:B2_B3_cmp} for samples of generators trained with $\lambda_{adv}=0$ and $\lambda_{adv}=0.040$ respectively. If only the $L_1$ reconstruction loss is used, then the hallucinated part looks fuzzy and unrealistic. Enabling the discriminator clearly has a sharpening effect on the output, although the results start to look excessively decorated at times. It seems that the trade-off between the reconstruction and adversarial loss functions should be more finely investigated.

\begin{figure*}[tp]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
      \centering
      \includegraphics[width=0.95\linewidth]{B3_low_rec3b}
      \caption{Low reconstruction error.}
      \vspace{0.2cm}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
      \centering
      \includegraphics[width=0.95\linewidth]{B3_high_rec2}
      \caption{High reconstruction error.}
  \end{subfigure}
  \caption{Examples of outpainting on Places365 selected for varying MSEs (lower is better), revealing semantic differences within the images.}
  \label{fig:low_high_mse}
\end{figure*}

\begin{figure*}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\textwidth]{B4_samples_test}
  \end{adjustbox}
  \caption{Qualitative illustration of artwork outpainting on WikiArt.}
  \label{fig:B4_samples}
\end{figure*}

\begin{figure}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=\columnwidth]{B4_high_D}
  \end{adjustbox}
  \caption{Examples of outpainting on WikiArt selected for high discriminator output values, indicating a bias towards highly decorated paintings.}
  \label{fig:B4_high_D}
\end{figure}

\textbf{Variation in reconstruction quality} \hspace{0.3cm}
See Figure \ref{fig:low_high_mse} for samples where the MSE between the output and ground truth is either particularly low or high, when including the adversarial loss. It seems that 'smooth' images such as landscapes perform best, while highly detailed images including indoor scenes perform worst. This is understandable: if the dimensions of objects within the image are smaller than what is being omitted, they become impossible for the outpainter to predict.

\textbf{Artwork outpainting} \hspace{0.3cm}
See Figure \ref{fig:B4_samples} for a few examples of generative outpainting performed on the WikiArt validation- and test sets. In this application, we answer the question \textit{'What would the artist have drawn if he/she had a bigger canvas?'}. The results look comparatively accurate and visually pleasing, for which we think the reason is that 'imperfections' in art (to the extent that term is even well-defined) are much less bothersome than in natural imagery. It is also interesting to observe that when the output's realism $D(G(x))$ is maximized, a bias towards specific types of artwork content and/or genres can be perceived as in Figure \ref{fig:B4_high_D}.

\begin{figure*}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=0.9\textwidth]{B34_recursive}
  \end{adjustbox}
  \caption{Recursive outpainting on both natural photos and artwork, revealing some glitches but also intriguing 'eigenmodes' of the network.}
  \label{fig:B34_recursive}
\end{figure*}

\subsection{Recursive outpainting}

\hspace{\parindent} In contrast to inpainting, outpainting does not have to be performed just once; in theory, there is no limit as to how many times we can extrapolate a single image. Figure \ref{fig:B34_recursive} reveals an interesting aspect of the outpainting network: it seems that given enough iterations, the images eventually start to converge to some kind of 'eigenmode' of the generator. We moreover observe that the painting of a park with flowers seems to slowly morph into a landscape with clouds as we keep hallucinating outwards, suggesting that this scenery must appear (disproportionately) often in the training set.

\begin{figure*}[tp]
\centering
  \begin{adjustbox}{center}
  \includegraphics[width=0.8\textwidth]{singan}
  \end{adjustbox}
  \caption{Qualitative comparison of outpainting without adversarial loss followed by SinGAN harmonization (which has an adversarial aspect by nature), versus direct adversarial outpainting with the proposed GAN.}
  \label{fig:singan}
\end{figure*}

\subsection{Harmonization}

\hspace{\parindent} Our second method for outpainting introduces an additional step that involves employing SinGAN as described earlier. The biggest drawback of this approach is that it takes around an hour to train SinGAN on a single input image, in contrast to the outpainter itself which is a model that can simply be applied anytime once it is trained on a dataset. Nevertheless, we tested out the joint harmonization and super-resolution process on several images that demonstrate its potential, as seen in Figure \ref{fig:singan}. When applied on the output of the reconstruction loss minimizer, it has a sharpening effect. Furthermore, despite the fact that the end result still lacks photorealism, we observe fewer glitches than the first approach which uses an adversarially trained GAN directly. Arbitrarily large resolutions could in principle be supported by SinGAN, although in practice a huge amount of GPU memory ($>12$GB) is needed to scale beyond a maximum image dimension of around 500 pixels.

\section{TODO: CONCLUSION}

\hspace{\parindent} Image outpainting is a novel but exciting idea that holds promise, especially when cascaded with SinGAN to further increase the output fidelity. The models trained in this project still contain some glitches, but we believe these could be alleviated by closer investigations into the subject. Non-photorealistic images such as artwork seem to produce convincing results, which we largely attribute to human judgement becoming more permissive rather than to a better-performing model.

\section{TODO: FUTURE WORK}

\hspace{\parindent}  Other than architectural improvements, possible directions for future research include:
\begin{itemize}
  \item While enabling the discriminator in this project significantly sharpened the outpainting results, the training stability could be better and the model was not very successful in enforcing natural object semantics across the image. Instead of a single discriminator, utilizing both a global and local variant might increase the overall consistency of generated images as well as improve the realism of smaller-scale structures \cite{Iizuka2017}.
  \item At the present time, it is unknown how the model reacts to slight variations in the input space. Hence, video outpainting presents a set of new interesting challenges, mostly related to temporal consistency of the hallucinations.
\end{itemize}

% \begin{acknowledgments}
% \vspace{-0.11cm}
\section*{ACKNOWLEDGEMENTS}

\hspace{\parindent} We would like to thank Prof. Jacob Whitehill for the opportunity to conduct this research project whilst giving critical feedback and opportunities for peer review  and discussion, and providing a great learning environment in his \textit{Deep Learning} course.

% \end{acknowledgments}

\bibliographystyle{unsrt}
\bibliography{bib}

\end{document}

### 2020-05-04 local/forward.py
LocalDiscriminator is now part of ContextDiscriminator, where both weights are averaged

@@ -1,10 +1,9 @@
-# Basile Van Hoorick, Jan 2020
 '''
 Hallucinates beyond all four edges of an image, increasing both dimensions by 50%.
-The outpainting process interally converts 128x128 to 192x192, after which the generated output is upscaled.
+The outpainting process internally converts 128x128 to 192x192, after which the generated output is upscaled.
 Then, the original input is blended onto the result for optimal fidelity.
-Example usage:
-python forward.py input.jpg output.jpg
+
+Example usage: python forward.py input.jpg output.jpg
 '''
 
 if __name__ == '__main__':

### 2020-05-04 local/local_model.py

@@ -2,99 +2,64 @@ import torch
 import torch.nn as nn
 import torch.nn.functional as F
 
-from local import outpainting
-
-
-class Flatten(nn.Module):
-    def __init__(self):
-        super(Flatten, self).__init__()
-
-    def forward(self, x):
-        return x.view(x.shape[0], -1)
-
-
-class Concatenate(nn.Module):
-    def __init__(self, dim=-1):
-        super(Concatenate, self).__init__()
-        self.dim = dim
-
-    def forward(self, x):
-        return torch.cat(x, dim=self.dim)
+from local import layers
 
 
 class CompletionNetwork(nn.Module):
     def __init__(self):
         super(CompletionNetwork, self).__init__()
-        # input_shape: (None, 4, img_h, img_w)
         self.conv1 = nn.Conv2d(4, 64, kernel_size=5, stride=1, padding=2)
         self.bn1 = nn.BatchNorm2d(64)
         self.act1 = nn.ReLU()
-        # input_shape: (None, 64, img_h, img_w)
         self.conv2 = nn.Conv2d(64, 128, kernel_size=3, stride=2, padding=1)
         self.bn2 = nn.BatchNorm2d(128)
         self.act2 = nn.ReLU()
-        # input_shape: (None, 128, img_h//2, img_w//2)
         self.conv3 = nn.Conv2d(128, 128, kernel_size=3, stride=1, padding=1)
         self.bn3 = nn.BatchNorm2d(128)
         self.act3 = nn.ReLU()
-        # input_shape: (None, 128, img_h//2, img_w//2)
         self.conv4 = nn.Conv2d(128, 256, kernel_size=3, stride=2, padding=1)
         self.bn4 = nn.BatchNorm2d(256)
         self.act4 = nn.ReLU()
-        # input_shape: (None, 256, img_h//4, img_w//4)
         self.conv5 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
         self.bn5 = nn.BatchNorm2d(256)
         self.act5 = nn.ReLU()
-        # input_shape: (None, 256, img_h//4, img_w//4)
         self.conv6 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
         self.bn6 = nn.BatchNorm2d(256)
         self.act6 = nn.ReLU()
-        # input_shape: (None, 256, img_h//4, img_w//4)
         self.conv7 = nn.Conv2d(256, 256, kernel_size=3, stride=1, dilation=2, padding=2)
[…]

### 2020-05-04 local/outpainting.py

@@ -1,35 +1,22 @@
-# Basile Van Hoorick, Jan 2020
-
-import copy
-import cv2
 import glob
 import matplotlib.patches as patches
 import matplotlib.pyplot as plt
 import numpy as np
-import pickle
-import random
-import scipy
 import shutil
 import skimage
-import time
 import torch
-import torch.nn.functional as F
-import torchvision
 import os
-from bisect import bisect_left, bisect_right
 from collections import defaultdict, OrderedDict
 from html4vision import Col, imagetable
 from PIL import Image
 from scipy.ndimage.morphology import distance_transform_edt
-from skimage import io
-from torch import nn, optim
+from torch import nn
 from torch.autograd import Variable
-from torchvision import datasets, transforms, models, utils
 from torchvision.utils import save_image
 from torch.utils.data import Dataset, DataLoader
-from tqdm import tqdm
 
 from local import util
+from local import layers
 
 input_size = 128
 output_size = 192
@@ -39,9 +26,9 @@ patch_h = output_size // 8
 patch = (1, patch_h, patch_w)
 
 
-class CEGenerator(nn.Module):
+class Generator(nn.Module):
     def __init__(self, channels=3, extra_upsample=False):
-        super(CEGenerator, self).__init__()
+        super(Generator, self).__init__()
 
         def downsample(in_feat, out_feat, normalize=True):
             layers = [nn.Conv2d(in_feat, out_feat, 4, stride=2, padding=1)]
@@ -93,9 +80,9 @@ class CEGenerator(nn.Module):
         return self.model(x)
 
 
-class CEGlobalDiscriminator(nn.Module):
+class GlobalDiscriminator(nn.Module):
     def __init__(self, channels=3):
-        super(CEGlobalDiscriminator, self).__init__()
+        super(GlobalDiscriminator, self).__init__()
         self.output_shape = (24, 24)
 
         def discriminator_block(in_filters, out_filters, stride, normalize):
@@ -117,9 +104,68 @@ class CEGlobalDiscriminator(nn.Module):
         self.model = nn.Sequential(*layers)
 
     def forward(self, img):
-        x = self.model(img)
-        print('CEDiscriminator shape', x.shape)
         return self.model(img)
+
+
+class LocalDiscriminator(nn.Module):
+    def __init__(self, mask, channels=3):
+        super(LocalDiscriminator, self).__init__()
+        self.output_shape = (24, 24)
+
+        def discriminator_block(in_filters, out_filters, stride, normalize):
[…]

### 2020-05-04 local/train.py

@@ -1,7 +1,10 @@
-# Basile Van Hoorick, Jan 2020
+import pickle
 import torch
+import torchvision
+from torch import nn, optim
+
 from local import local_model
-from local.outpainting import *
+from local import outpainting
 
 '''
 Edit the paths here and run to train the GAN.
@@ -20,62 +23,45 @@ if __name__ == '__main__':
     test_dir = '../test'
 
     # Define datasets & transforms
-    my_tf = transforms.Compose([
-            transforms.Resize(output_size),
-            transforms.CenterCrop(output_size),
-            transforms.RandomHorizontalFlip(),
-            transforms.ToTensor()])
+    my_tf = torchvision.transforms.Compose([
+            torchvision.transforms.Resize(outpainting.output_size),
+            torchvision.transforms.CenterCrop(outpainting.output_size),
+            torchvision.transforms.RandomHorizontalFlip(),
+            torchvision.transforms.ToTensor()])
     batch_size = 4
-    train_data = CEImageDataset(train_dir, my_tf, output_size, input_size, outpaint=True)
-    val_data = CEImageDataset(val_dir, my_tf, output_size, input_size, outpaint=True)
-    test_data = CEImageDataset(test_dir, my_tf, output_size, input_size, outpaint=True)
-    train_loader = DataLoader(train_data, batch_size=batch_size, shuffle=True, num_workers=1)
-    val_loader = DataLoader(val_data, batch_size=batch_size, shuffle=True, num_workers=1)
-    test_loader = DataLoader(test_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    train_data = outpainting.CEImageDataset(train_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    val_data = outpainting.CEImageDataset(val_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    test_data = outpainting.CEImageDataset(test_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    train_loader = outpainting.DataLoader(train_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    val_loader = outpainting.DataLoader(val_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    test_loader = outpainting.DataLoader(test_data, batch_size=batch_size, shuffle=True, num_workers=1)
     print('train:', len(train_data), 'val:', len(val_data), 'test:', len(test_data))
 
[…]

### 2020-05-04 local/util.py

@@ -1,5 +1,4 @@
 import torch
-import torchvision
 
 
 def gen_mask(shape, input_size=128, output_size=192):
@@ -10,7 +9,7 @@ def gen_mask(shape, input_size=128, output_size=192):
     :param shape: Shape of mask tensor to be generated like (num, channel, height, width)
     :param input_size:
     :param output_size:
-    :returns: Mask tensor where pixels indicating mask are filled with 1.0
+    :returns: Mask tensor where pixels indicating mask are filled with 1. and rest are 0.
     """
     expand_size = (output_size - input_size) // 2
     mask = torch.zeros(shape)

### 2020-05-05 local/outpainting.py
Added loss plots

@@ -403,9 +403,24 @@ def get_adv_weight(adv_weight, epoch):
 
 def train(G_net, D_net, device, criterion_pxl, criterion_D, optimizer_G, optimizer_D, data_loaders,
           model_save_path, html_save_path, n_epochs=200, start_epoch=0, adv_weight=0.001):
-    '''
-    Based on Context Encoder implementation in PyTorch.
-    '''
+    """
+    Outpainting GAN training loop based on Context Encoder implementation in PyTorch.
+
+    :param G_net:
+    :param D_net:
+    :param device:
+    :param criterion_pxl:
+    :param criterion_D:
+    :param optimizer_G:
+    :param optimizer_D:
+    :param data_loaders:
+    :param model_save_path:
+    :param html_save_path:
+    :param n_epochs:
+    :param start_epoch:
+    :param adv_weight:
+    :return:
+    """
     Tensor = torch.cuda.FloatTensor
     hist_loss = defaultdict(list)
     
@@ -454,9 +469,7 @@ def train(G_net, D_net, device, criterion_pxl, criterion_D, optimizer_G, optimiz
                 #     loss_pxl = criterion_pxl(outputs, masked_parts)  # inpaint: compare center part only
                 # else:
                 loss_pxl = criterion_pxl(outputs, imgs)  # outpaint: compare to full ground truth
-                y_hat = D_net(outputs, mask)
-
-                loss_adv = criterion_D(y_hat, valid)
+                loss_adv = criterion_D(D_net(outputs, mask), valid)
                 # Total loss
                 cur_adv_weight = get_adv_weight(adv_weight, epoch)
                 loss_G = (1 - cur_adv_weight) * loss_pxl + cur_adv_weight * loss_adv
@@ -473,8 +486,8 @@ def train(G_net, D_net, device, criterion_pxl, criterion_D, optimizer_G, optimiz
                 # if not(outpaint):
                 #     real_loss = criterion_D(D_net(masked_parts), valid) # inpaint: check center part only
                 # else:
+                # TODO: need to clarify real vs fake loss here
                 real_loss = criterion_D(D_net(imgs, mask), valid)  # outpaint: check full ground truth
-
                 fake_loss = criterion_D(D_net(outputs.detach(), mask), fake)
                 loss_D = 0.5 * (real_loss + fake_loss)
                 if phase == 'train':

### 2020-05-05 local/train.py

@@ -2,6 +2,7 @@ import pickle
 import torch
 import torchvision
 from torch import nn, optim
+import matplotlib.pyplot as plt
 
 from local import local_model
 from local import outpainting
@@ -64,4 +65,35 @@ if __name__ == '__main__':
 
     # Save loss history and final generator
     pickle.dump(hist_loss, open('hist_loss.p', 'wb'))
+
+    plt.plot(hist_loss['train_pxl'])
+    plt.xlabel('epochs')
+    plt.ylabel('L1 loss')
+    plt.savefig('train_pxl.png')
+
+    plt.plot(hist_loss['train_adv'])
+    plt.xlabel('epochs')
+    plt.ylabel('MSE loss')
+    plt.savefig('train_adv.png')
+
+    plt.plot(hist_loss['train_D'])
+    plt.xlabel('epochs')
+    plt.ylabel('context discriminator loss')
+    plt.savefig('train_D.png')
+
+    plt.plot(hist_loss['val_pxl'])
+    plt.xlabel('epochs')
+    plt.ylabel('L1 loss')
+    plt.savefig('val_pxl.png')
+
+    plt.plot(hist_loss['val_adv'])
+    plt.xlabel('epochs')
+    plt.ylabel('MSE loss')
+    plt.savefig('val_adv.png')
+
+    plt.plot(hist_loss['val_D'])
+    plt.xlabel('epochs')
+    plt.ylabel('context discriminator loss')
+    plt.savefig('val_D.png')
+
     torch.save(G_net.state_dict(), 'generator_final.pt')

### 2020-05-05 tex/paper.tex
Added paper template TeX files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2017 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[cs541,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{cs541} with
% \usepackage[nohyperref]{cs541} above.
\usepackage{hyperref}

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\usepackage[accepted]{cs541}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Title of My Paper}

\begin{document}

\twocolumn[
\icmltitle{Title of My Paper}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2017
% package.

% list of affiliations. the first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% you can specify symbols, otherwise they are numbered in order
% ideally, you should not use this facility. affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{wpi}
\icmlauthor{Bauiu C.~Yyyy}{wpi}
\end{icmlauthorlist}

\icmlaffiliation{wpi}{Worcester Polytechnic Institute}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@wpi.edu}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
%\footnotetext{hi}

\begin{abstract} 
Describe {\bf briefly} the computational problem you tackled, the approach you explored, the analyses you performed, and the results you obtained.
Point out advantages of your approach compared to prior approaches (if any).
\end{abstract}

\section{Introduction}
{\bf Problem before solution}:
Begin by describing a (computational) {\bf problem} and why the problem is {\bf important}. If previous research has
explored plausible solutions to solve the problem, then point out how these approaches may be lacking. Then briefly {\bf motivate}
why a new approach (the approach you explore in this paper) is worth exploring. Don't go into too much detail yet how it works -- that will
be left for Section \ref{sec:proposed_method}).

\subsection{Research contributions}
Describe clearly and concisely what your paper {\bf uniquely} contributes to the research community, i.e., that has never been done before.

\section{Related Work}
Describe previous approaches (in somewhat greater detail than the introduction) to tackling the problem. Pick any citation style you prefer and use it
consistently (here's a random citation \cite{mitchell80}). Explain how previous work may be lacking in certain ways, and use your critical review
of prior work to further motivate your research.

\section{Proposed Method}
\label{sec:proposed_method}
Describe the computational approach -- based obviously on neural networks -- that you took to tackle the problem.

\section{Experiment}
Describe the computational experiments you conducted to validate the approach you took.

\section{Results}
Describe the results of the experiments, including their immediate implications (e.g., ``the result suggests that technique A performs better
than technique B''). If your work is purely theoretical, then this section (as well as the previous section) might be replaced with mathematical proofs.

\section{Discussion}
Describe limitations of your work as well as further-ranging implications (e.g., ``our work suggests that doing XYZ in general may be a useful approach to...'').

\section{Conclusions and Future Work}
Briefly summarize the key findings your paper and point out interesting directions for future inquiry.

\bibliography{example_paper}
\bibliographystyle{cs541}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was
% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
% slightly modified from the 2009 version by Kiri Wagstaff and 
% Sam Roweis's 2008 version, which is slightly modified from 
% Prasad Tadepalli's 2007 version which is a lightly 
% changed version of the previous year's version by Andrew Moore, 
% which was in turn edited from those of Kristian Kersting and 
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2020-05-07 local/train.py
Update train.py

@@ -4,8 +4,8 @@ import torchvision
 from torch import nn, optim
 import matplotlib.pyplot as plt
 
-from local import local_model
-from local import outpainting
+import local_model
+import outpainting
 
 '''
 Edit the paths here and run to train the GAN.

### 2020-05-07 local/outpainting.py
Update outpainting.py

@@ -15,8 +15,8 @@ from torch.autograd import Variable
 from torchvision.utils import save_image
 from torch.utils.data import Dataset, DataLoader
 
-from local import util
-from local import layers
+import util
+import layers
 
 input_size = 128
 output_size = 192

### 2020-05-07 local/local_model.py
Update local_model.py

@@ -2,7 +2,7 @@ import torch
 import torch.nn as nn
 import torch.nn.functional as F
 
-from local import layers
+import layers
 
 
 class CompletionNetwork(nn.Module):

### 2020-05-07 local/outpainting.py
Fixed error caused by missing mask channel on passing image into generate_html

@@ -344,7 +344,7 @@ def finish_inpaint(imgs, outputs):
     return result
 
 
-def generate_html(G_net, D_net, device, data_loaders, html_save_path, max_rows=64, outpaint=True):
+def generate_html(G_net, D_net, mask, device, data_loaders, html_save_path, max_rows=64):
     '''
     Visualizes one batch from both the training and validation sets.
     Images are stored in the specified HTML file path.
@@ -359,13 +359,13 @@ def generate_html(G_net, D_net, device, data_loaders, html_save_path, max_rows=6
     # Evaluate examples
     for phase in ['train', 'val']:
         imgs, masked_imgs, masked_parts = next(iter(data_loaders[phase]))
-        masked_imgs = masked_imgs.to(device)
+        masked_imgs = torch.cat((masked_imgs, mask), dim=1).to(device)
         outputs = G_net(masked_imgs)
         masked_imgs = masked_imgs.cpu()
-        if not(outpaint):
-            results = finish_inpaint(imgs, outputs.cpu())
-        else:
-            results = outputs.cpu()
+        # if not outpaint:
+        #     results = finish_inpaint(imgs, outputs.cpu())
+        # else:
+        results = outputs.cpu()
         # Store images
         for i in range(min(imgs.shape[0], max_rows)):
             save_image(masked_imgs[i], html_save_path + '/images/' + phase + '_' + str(i) + '_masked.jpg')
@@ -509,7 +509,7 @@ def train(G_net, D_net, device, criterion_pxl, criterion_D, optimizer_G, optimiz
                     os.makedirs(model_save_path)
                 torch.save(G_net.state_dict(), model_save_path + '/G_' + str(epoch) + '.pt')
                 torch.save(D_net.state_dict(), model_save_path + '/D_' + str(epoch) + '.pt')
-                generate_html(G_net, D_net, device, data_loaders, html_save_path + '/' + str(epoch))
+                generate_html(G_net, D_net, mask, device, data_loaders, html_save_path + '/' + str(epoch))
 
             # Store & print statistics
             cur_loss_pxl = running_loss_pxl / batches_done

### 2020-05-07 local/outpainting.py
generate_html creates it's own mask with masked_imgs shape[0] to match batch size

@@ -44,7 +44,7 @@ class Generator(nn.Module):
             layers.append(nn.ReLU())
             return layers
 
-        if not(extra_upsample):
+        if not extra_upsample:
             self.model = nn.Sequential(
                 *downsample(channels, 64, normalize=False),
                 *downsample(64, 64),
@@ -144,10 +144,7 @@ class ContextDiscriminator(nn.Module):
         assert(local_input_shape == global_input_shape)
         self.output_shape = (1,)
 
-        # self.model_ld = LocalDiscriminator(local_input_shape)
         self.model_ld = LocalDiscriminator(local_input_shape)
-
-        # self.model_gd = GlobalDiscriminator(global_input_shape, arc=arc)
         self.model_gd = GlobalDiscriminator()
 
         # TODO: Remove, this stuff gets handled afterwards
@@ -263,7 +260,7 @@ def load_model(model_path):
     new_state_dict = OrderedDict()
     for k, v in state_dict.items():
         if 'module' in k:
-            name = k[7:] # remove 'module'
+            name = k[7:]  # remove 'module'
         else:
             name = k
         new_state_dict[name] = v
@@ -344,7 +341,7 @@ def finish_inpaint(imgs, outputs):
     return result
 
 
-def generate_html(G_net, D_net, mask, device, data_loaders, html_save_path, max_rows=64):
+def generate_html(G_net, D_net, device, data_loaders, html_save_path, max_rows=64):
     '''
     Visualizes one batch from both the training and validation sets.
     Images are stored in the specified HTML file path.
@@ -359,6 +356,8 @@ def generate_html(G_net, D_net, mask, device, data_loaders, html_save_path, max_
     # Evaluate examples
     for phase in ['train', 'val']:
         imgs, masked_imgs, masked_parts = next(iter(data_loaders[phase]))
+        mask_shape = (masked_imgs.shape[0], 1, masked_imgs.shape[2], masked_imgs.shape[3])
+        mask = util.gen_mask(mask_shape).to(device)
         masked_imgs = torch.cat((masked_imgs, mask), dim=1).to(device)
         outputs = G_net(masked_imgs)
         masked_imgs = masked_imgs.cpu()
@@ -445,11 +444,12 @@ def train(G_net, D_net, device, criterion_pxl, criterion_D, optimizer_G, optimiz
                 # Adversarial ground truths
                 valid = Variable(Tensor(imgs.shape[0], *patch).fill_(1.0), requires_grad=False).to(device)
[…]

### 2020-05-07 local/outpainting.py
Fixed masked image dimension and last channel

@@ -193,7 +193,7 @@ def blend_result(output_img, input_img, blend_width=8):
         in_width, in_height = input_img.shape[1], input_img.shape[0]
         out_width, out_height = int(in_width / in_factor), int(in_height / in_factor)
         output_img = skimage.transform.resize(output_img, (out_height, out_width), anti_aliasing=True)
-    
+
     # Construct source mask
     src_mask = np.zeros((output_size, output_size))
     src_mask[expand_size+1:-expand_size-1, expand_size+1:-expand_size-1] = 1 # 1 extra pixel for safety
@@ -201,13 +201,13 @@ def blend_result(output_img, input_img, blend_width=8):
     src_mask = np.minimum(src_mask, 1)
     src_mask = skimage.transform.resize(src_mask, (out_height, out_width), anti_aliasing=True)
     src_mask = np.tile(src_mask[:, :, np.newaxis], (1, 1, 3))
-    
+
     # Pad input
     input_pad = np.zeros((out_height, out_width, 3))
     x1 = (out_width - in_width) // 2
     y1 = (out_height - in_height) // 2
     input_pad[y1:y1+in_height, x1:x1+in_width, :] = input_img
-    
+
     # Merge
     blended = input_pad * src_mask + output_img * (1 - src_mask)
 
@@ -284,7 +284,7 @@ def weights_init_normal(m):
 
 
 class CEImageDataset(Dataset):
-    
+
     def __init__(self, root, transform, output_size=192, input_size=128, outpaint=True):
         self.transform = transform
         self.output_size = output_size
@@ -296,7 +296,7 @@ class CEImageDataset(Dataset):
         """Mask center part of image"""
         # Get upper-left pixel coordinate
         i = (self.output_size - self.input_size) // 2
-        
+
         if not self.outpaint:
             masked_part = img[:, i:i + self.input_size, i:i + self.input_size]
             masked_img = img.clone()
@@ -319,7 +319,7 @@ class CEImageDataset(Dataset):
         except:
             # Likely corrupt image file, so generate black instead
             img = torch.zeros((3, self.output_size, self.output_size))
-            
+
         masked_img, masked_part = self.apply_center_mask(img)
 
         return img, masked_img, masked_part
@@ -344,7 +344,7 @@ def finish_inpaint(imgs, outputs):
     return result
 
 
-def generate_html(G_net, D_net, device, data_loaders, html_save_path, max_rows=64, outpaint=True):
[…]

### 2020-05-08 util/getNimages.sh
Get subset with N images

@@ -1,0 +1,6 @@
+#!/bin/bash
+N=164250;
+for i in ./test/*.jpg; do
+  [ "$((N--))" = 0 ] && break
+  cp $i ./baseline_half/test_half
+done

### 2020-05-08 outpainting.py
Fixed masked image dimension and last channel

@@ -1,0 +1,532 @@
+import glob
+import matplotlib.patches as patches
+import matplotlib.pyplot as plt
+import numpy as np
+import shutil
+import skimage
+import torch
+import os
+from collections import defaultdict, OrderedDict
+from html4vision import Col, imagetable
+from PIL import Image
+from scipy.ndimage.morphology import distance_transform_edt
+from torch import nn
+from torch.autograd import Variable
+from torchvision.utils import save_image
+from torch.utils.data import Dataset, DataLoader
+
+import util
+import layers
+
+input_size = 128
+output_size = 192
+expand_size = (output_size - input_size) // 2
+patch_w = output_size // 8
+patch_h = output_size // 8
+patch = (1, patch_h, patch_w)
+
+
+class Generator(nn.Module):
+    def __init__(self, channels=3, extra_upsample=False):
+        super(Generator, self).__init__()
+
+        def downsample(in_feat, out_feat, normalize=True):
+            layers = [nn.Conv2d(in_feat, out_feat, 4, stride=2, padding=1)]
+            if normalize:
+                layers.append(nn.BatchNorm2d(out_feat, 0.8))
+            layers.append(nn.LeakyReLU(0.2))
+            return layers
+
+        def upsample(in_feat, out_feat, normalize=True):
+            layers = [nn.ConvTranspose2d(in_feat, out_feat, 4, stride=2, padding=1)]
+            if normalize:
+                layers.append(nn.BatchNorm2d(out_feat, 0.8))
+            layers.append(nn.ReLU())
+            return layers
+
+        if not(extra_upsample):
+            self.model = nn.Sequential(
+                *downsample(channels, 64, normalize=False),
+                *downsample(64, 64),
+                *downsample(64, 128),
+                *downsample(128, 256),
+                *downsample(256, 512),
+                nn.Conv2d(512, 4000, 1),
+                *upsample(4000, 512),
+                *upsample(512, 256),
+                *upsample(256, 128),
+                *upsample(128, 64),
+                nn.Conv2d(64, channels, 3, 1, 1),
+                nn.Tanh()
+            )
+        else:
+            self.model = nn.Sequential(
+                *downsample(channels, 64, normalize=False),
+                *downsample(64, 64),
+                *downsample(64, 128),
+                *downsample(128, 256),
+                *downsample(256, 512),
[…]

### 2020-05-08 outpainting.py
Delete outpainting.py

@@ -1,532 +1,0 @@
-import glob
-import matplotlib.patches as patches
-import matplotlib.pyplot as plt
-import numpy as np
-import shutil
-import skimage
-import torch
-import os
-from collections import defaultdict, OrderedDict
-from html4vision import Col, imagetable
-from PIL import Image
-from scipy.ndimage.morphology import distance_transform_edt
-from torch import nn
-from torch.autograd import Variable
-from torchvision.utils import save_image
-from torch.utils.data import Dataset, DataLoader
-
-import util
-import layers
-
-input_size = 128
-output_size = 192
-expand_size = (output_size - input_size) // 2
-patch_w = output_size // 8
-patch_h = output_size // 8
-patch = (1, patch_h, patch_w)
-
-
-class Generator(nn.Module):
-    def __init__(self, channels=3, extra_upsample=False):
-        super(Generator, self).__init__()
-
-        def downsample(in_feat, out_feat, normalize=True):
-            layers = [nn.Conv2d(in_feat, out_feat, 4, stride=2, padding=1)]
-            if normalize:
-                layers.append(nn.BatchNorm2d(out_feat, 0.8))
-            layers.append(nn.LeakyReLU(0.2))
-            return layers
-
-        def upsample(in_feat, out_feat, normalize=True):
-            layers = [nn.ConvTranspose2d(in_feat, out_feat, 4, stride=2, padding=1)]
-            if normalize:
-                layers.append(nn.BatchNorm2d(out_feat, 0.8))
-            layers.append(nn.ReLU())
-            return layers
-
-        if not(extra_upsample):
-            self.model = nn.Sequential(
-                *downsample(channels, 64, normalize=False),
-                *downsample(64, 64),
-                *downsample(64, 128),
-                *downsample(128, 256),
-                *downsample(256, 512),
-                nn.Conv2d(512, 4000, 1),
-                *upsample(4000, 512),
-                *upsample(512, 256),
-                *upsample(256, 128),
-                *upsample(128, 64),
-                nn.Conv2d(64, channels, 3, 1, 1),
-                nn.Tanh()
-            )
-        else:
-            self.model = nn.Sequential(
-                *downsample(channels, 64, normalize=False),
-                *downsample(64, 64),
-                *downsample(64, 128),
-                *downsample(128, 256),
-                *downsample(256, 512),
[…]

### 2020-05-08 local/outpainting.py
Fixed masked image dimension and last channel

@@ -44,7 +44,7 @@ class Generator(nn.Module):
             layers.append(nn.ReLU())
             return layers
 
-        if not extra_upsample:
+        if not(extra_upsample):
             self.model = nn.Sequential(
                 *downsample(channels, 64, normalize=False),
                 *downsample(64, 64),
@@ -144,7 +144,10 @@ class ContextDiscriminator(nn.Module):
         assert(local_input_shape == global_input_shape)
         self.output_shape = (1,)
 
+        # self.model_ld = LocalDiscriminator(local_input_shape)
         self.model_ld = LocalDiscriminator(local_input_shape)
+
+        # self.model_gd = GlobalDiscriminator(global_input_shape, arc=arc)
         self.model_gd = GlobalDiscriminator()
 
         # TODO: Remove, this stuff gets handled afterwards
@@ -190,7 +193,7 @@ def blend_result(output_img, input_img, blend_width=8):
         in_width, in_height = input_img.shape[1], input_img.shape[0]
         out_width, out_height = int(in_width / in_factor), int(in_height / in_factor)
         output_img = skimage.transform.resize(output_img, (out_height, out_width), anti_aliasing=True)
-    
+
     # Construct source mask
     src_mask = np.zeros((output_size, output_size))
     src_mask[expand_size+1:-expand_size-1, expand_size+1:-expand_size-1] = 1 # 1 extra pixel for safety
@@ -198,13 +201,13 @@ def blend_result(output_img, input_img, blend_width=8):
     src_mask = np.minimum(src_mask, 1)
     src_mask = skimage.transform.resize(src_mask, (out_height, out_width), anti_aliasing=True)
     src_mask = np.tile(src_mask[:, :, np.newaxis], (1, 1, 3))
-    
+
     # Pad input
     input_pad = np.zeros((out_height, out_width, 3))
     x1 = (out_width - in_width) // 2
     y1 = (out_height - in_height) // 2
     input_pad[y1:y1+in_height, x1:x1+in_width, :] = input_img
-    
+
     # Merge
     blended = input_pad * src_mask + output_img * (1 - src_mask)
 
@@ -260,7 +263,7 @@ def load_model(model_path):
     new_state_dict = OrderedDict()
     for k, v in state_dict.items():
         if 'module' in k:
-            name = k[7:]  # remove 'module'
+            name = k[7:] # remove 'module'
         else:
             name = k
         new_state_dict[name] = v
[…]

### 2020-05-08 residual/forward.py
refactored model to work with res addition

@@ -1,0 +1,24 @@
+'''
+Hallucinates beyond all four edges of an image, increasing both dimensions by 50%.
+The outpainting process internally converts 128x128 to 192x192, after which the generated output is upscaled.
+Then, the original input is blended onto the result for optimal fidelity.
+
+Example usage: python forward.py input.jpg output.jpg
+'''
+
+if __name__ == '__main__':
+
+    import sys
+    from local.outpainting import *
+
+    print("PyTorch version: ", torch.__version__)
+    print("Torchvision version: ", torchvision.__version__)
+
+    src_file = sys.argv[1]
+    dst_file = sys.argv[2]
+    gen_model = load_model('generator_final.pt')
+    print('Source file: ' + src_file + '...')
+    input_img = plt.imread(src_file)[:, :, :3]
+    output_img, blended_img = perform_outpaint(gen_model, input_img)
+    plt.imsave(dst_file, blended_img)
+    print('Destination file: ' + dst_file + ' written')

### 2020-05-08 residual/outpainting.py

@@ -1,0 +1,548 @@
+import glob
+import matplotlib.patches as patches
+import matplotlib.pyplot as plt
+import numpy as np
+import shutil
+import skimage
+import torch
+import os
+from collections import defaultdict, OrderedDict
+from html4vision import Col, imagetable
+from PIL import Image
+from scipy.ndimage.morphology import distance_transform_edt
+from torch import nn
+from torch.autograd import Variable
+from torchvision.utils import save_image
+from torch.utils.data import Dataset, DataLoader
+
+import util
+import layers
+
+input_size = 128
+output_size = 192
+expand_size = (output_size - input_size) // 2
+patch_w = output_size // 8
+patch_h = output_size // 8
+patch = (1, patch_h, patch_w)
+
+
+class Generator(nn.Module):
+    def __init__(self, channels=3, extra_upsample=False):
+        super(Generator, self).__init__()
+        def downsample(in_feat, out_feat, normalize=True):
+            layers = [nn.Conv2d(in_feat, out_feat, 4, stride=2, padding=1)]
+            if normalize:
+                layers.append(nn.BatchNorm2d(out_feat, 0.8))
+            layers.append(nn.LeakyReLU(0.2))
+            return layers
+
+        def upsample(in_feat, out_feat, normalize=True):
+            layers = [nn.ConvTranspose2d(in_feat, out_feat, 4, stride=2, padding=1)]
+            if normalize:
+                layers.append(nn.BatchNorm2d(out_feat, 0.8))
+            layers.append(nn.ReLU())
+            return layers
+
+        self.down1 = downsample(channels, 64, normalize=True)
+
+        self.down2 = downsample(64, 64, normalize=True)
+
+        self.down3 = downsample(64, 128, normalize=True)
+
+        self.down4 = downsample(128, 256, normalize=True)
+
+        self.down5 = downsample(256, 512, normalize=True)
+
+        self.down6 = downsample(512, 4000, normalize=True)
+
+        self.down_middle = nn.Conv2d(512, 4000, 1)
+
+        self.up1 = upsample(4000, 512)
+        self.up2 = upsample(512, 256)
+        self.up3 = upsample(256, 128)
+        self.up4 = upsample(128, 64)
+
+
+        self.final_down = nn.Conv2d(64, channels, 3, 1, 1)
+        self.final_activation = nn.Tanh()
+
+    def forward(self, x):
+        z = self.down1[0](x)
+        z = self.down1[1](z)
+
+        for i in range(3):
[…]

### 2020-05-08 residual/train.py

@@ -1,0 +1,99 @@
+import pickle
+import torch
+import torchvision
+from torch import nn, optim
+import matplotlib.pyplot as plt
+
+import outpainting
+import residual_model
+
+'''
+Edit the paths here and run to train the GAN.
+Uses GPU:0 with CUDA (feel free to switch to CPU or use DataParallel).
+'''
+
+if __name__ == '__main__':
+    print("PyTorch version: ", torch.__version__)
+    print("Torchvision version: ", torchvision.__version__)
+
+    # Define paths
+    model_save_path = 'outpaint_models'
+    html_save_path = 'outpaint_html'
+    train_dir = '../train'
+    val_dir = '../val'
+    test_dir = '../test'
+
+    # Define datasets & transforms
+    my_tf = torchvision.transforms.Compose([
+            torchvision.transforms.Resize(outpainting.output_size),
+            torchvision.transforms.CenterCrop(outpainting.output_size),
+            torchvision.transforms.RandomHorizontalFlip(),
+            torchvision.transforms.ToTensor()])
+    batch_size = 4
+    train_data = outpainting.CEImageDataset(train_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    val_data = outpainting.CEImageDataset(val_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    test_data = outpainting.CEImageDataset(test_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    train_loader = outpainting.DataLoader(train_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    val_loader = outpainting.DataLoader(val_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    test_loader = outpainting.DataLoader(test_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    print('train:', len(train_data), 'val:', len(val_data), 'test:', len(test_data))
+
+    # Define model & device
+    device = torch.device('cuda:0')
+    G_net = residual_model.CompletionNetwork()
+    CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
+    G_net.apply(outpainting.weights_init_normal)
+    CD_net.apply(outpainting.weights_init_normal)
[…]

### 2020-05-08 residual/util.py

@@ -1,0 +1,21 @@
+import torch
+
+
+def gen_mask(shape, input_size=128, output_size=192):
+    """
+    Generate mask for given input and output size. Assumes square images.
+    Uses expand_size, which is distance from provided center of image to end of hallucination in pixels.
+
+    :param shape: Shape of mask tensor to be generated like (num, channel, height, width)
+    :param input_size:
+    :param output_size:
+    :returns: Mask tensor where pixels indicating mask are filled with 1. and rest are 0.
+    """
+    expand_size = (output_size - input_size) // 2
+    mask = torch.zeros(shape)
+    for i in range(shape[0]):
+        mask[i, :, expand_size:, :] = 1.
+        mask[i, :, :, :expand_size] = 1.
+        mask[i, :, -expand_size:, :] = 1.
+        mask[i, :, :, -expand_size:] = 1.
+    return mask

### 2020-05-08 residual/train.py
changed training generator

@@ -40,7 +40,7 @@ if __name__ == '__main__':
 
     # Define model & device
     device = torch.device('cuda:0')
-    G_net = residual_model.CompletionNetwork()
+    G_net = outpainting.Generator()
     CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
     G_net.apply(outpainting.weights_init_normal)
     CD_net.apply(outpainting.weights_init_normal)

### 2020-05-08 residual/outpainting.py
One resblock added

@@ -69,7 +69,7 @@ class Generator(nn.Module):
     def forward(self, x):
         z = self.down1[0](x)
         z = self.down1[1](z)
-
+        residual = z
         for i in range(3):
             z = self.down2[i](z)
         for i in range(3):
@@ -80,7 +80,7 @@ class Generator(nn.Module):
             z = self.down5[i](z)
         for i in range(3):
             z = self.down6[i](z)
-
+        z += residual
         z = self.down_middle(z)
 
         for i in range(3):

### 2020-05-08 residual/residual_model.py

@@ -5,79 +5,84 @@ import torch.nn.functional as F
 import layers
 
 
+class IdentityExpansion(nn.Module):
+    def __init__(self, num_filters, channels_in, stride):
+        super(IdentityExpansion, self).__init__()
+        # with kernel_size=1, max pooling is equivalent to identity mapping with stride
+        self.identity = nn.MaxPool2d(1, stride=stride)
+        self.num_zeros = num_filters - channels_in
+
+    def forward(self, x):
+        out = torch.nn.functional.pad(x, (0, 0, 0, 0, 0, self.num_zeros))
+        out = self.identity(out)
+        return out
+
 class CompletionNetwork(nn.Module):
     def __init__(self):
         super(CompletionNetwork, self).__init__()
         self.conv1 = nn.Conv2d(4, 64, kernel_size=5, stride=1, padding=2)
-        self.bn1 = nn.BatchNorm2d(64)
         self.act1 = nn.ReLU()
         self.conv2 = nn.Conv2d(64, 128, kernel_size=3, stride=2, padding=1)
-        self.bn2 = nn.BatchNorm2d(128)
         self.act2 = nn.ReLU()
         self.conv3 = nn.Conv2d(128, 128, kernel_size=3, stride=1, padding=1)
-        self.bn3 = nn.BatchNorm2d(128)
         self.act3 = nn.ReLU()
         self.conv4 = nn.Conv2d(128, 256, kernel_size=3, stride=2, padding=1)
-        self.bn4 = nn.BatchNorm2d(256)
         self.act4 = nn.ReLU()
         self.conv5 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
-        self.bn5 = nn.BatchNorm2d(256)
         self.act5 = nn.ReLU()
         self.conv6 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
-        self.bn6 = nn.BatchNorm2d(256)
         self.act6 = nn.ReLU()
         self.conv7 = nn.Conv2d(256, 256, kernel_size=3, stride=1, dilation=2, padding=2)
-        self.bn7 = nn.BatchNorm2d(256)
         self.act7 = nn.ReLU()
         self.conv8 = nn.Conv2d(256, 256, kernel_size=3, stride=1, dilation=4, padding=4)
-        self.bn8 = nn.BatchNorm2d(256)
         self.act8 = nn.ReLU()
[…]

### 2020-05-08 residual/train.py

@@ -40,7 +40,7 @@ if __name__ == '__main__':
 
     # Define model & device
     device = torch.device('cuda:0')
-    G_net = outpainting.Generator()
+    G_net = residual_model.CompletionNetwork()
     CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
     G_net.apply(outpainting.weights_init_normal)
     CD_net.apply(outpainting.weights_init_normal)

### 2020-05-08 residual/multiple_res_model.py
res now wokring

@@ -42,8 +42,6 @@ class CompletionNetwork(nn.Module):
         self.act10 = nn.ReLU()
         self.conv11 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
         self.act11 = nn.ReLU()
-        self.conv12 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
-
         self.act12 = nn.ReLU()
         # Here lies the latent space, with m feature maps of size n x n, total parameters m * n ^ 4
         self.deconv13 = nn.ConvTranspose2d(256, 128, kernel_size=4, stride=2, padding=1)
@@ -62,6 +60,7 @@ class CompletionNetwork(nn.Module):
         residual = x
         residual = IdentityExpansion(60,32,1).forward(residual)
 
+        res1 = x
         x = self.act1(self.conv1(x))
         x = self.act2(self.conv2(x))
 

### 2020-05-08 residual/multiple_res_model.py
changed residual

@@ -42,6 +42,8 @@ class CompletionNetwork(nn.Module):
         self.act10 = nn.ReLU()
         self.conv11 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
         self.act11 = nn.ReLU()
+        self.conv12 = nn.Conv2d(256, 256, kernel_size=3, stride=1, padding=1)
+
         self.act12 = nn.ReLU()
         # Here lies the latent space, with m feature maps of size n x n, total parameters m * n ^ 4
         self.deconv13 = nn.ConvTranspose2d(256, 128, kernel_size=4, stride=2, padding=1)
@@ -61,20 +63,31 @@ class CompletionNetwork(nn.Module):
         residual = IdentityExpansion(60,32,1).forward(residual)
 
         res1 = x
+        res1 = IdentityExpansion(124,0,2).forward(res1)
         x = self.act1(self.conv1(x))
         x = self.act2(self.conv2(x))
+        x+=res1
 
+        res2 = x
+        res2 = IdentityExpansion(128,0,2).forward(res2)
         x = self.act3(self.conv3(x))
         x = self.act4(self.conv4(x))
+        x+=res2
 
+        res3 = x
         x = self.act5(self.conv5(x))
         x = self.act6(self.conv6(x))
+        x+=res3
 
+        res4 = x
         x = self.act7(self.conv7(x))
         x = self.act8(self.conv8(x))
+        x+=res4
 
+        res5 = x
         x = self.act9(self.conv9(x))
         x = self.act10(self.conv10(x))
+        x+=res5
 
         x = self.act11(self.conv11(x))
         x = self.act12(self.conv12(x))

### 2020-05-08 context_residual/layers.py
Added residual blocks with context discriminator model version

@@ -1,0 +1,19 @@
+import torch
+from torch import nn
+
+
+class Flatten(nn.Module):
+    def __init__(self):
+        super(Flatten, self).__init__()
+
+    def forward(self, x):
+        return x.view(x.shape[0], -1)
+
+
+class Concatenate(nn.Module):
+    def __init__(self, dim=-1):
+        super(Concatenate, self).__init__()
+        self.dim = dim
+
+    def forward(self, x):
+        return torch.cat(x, dim=self.dim)

### 2020-05-08 context_residual/outpainting.py

@@ -1,0 +1,652 @@
+import glob
+import matplotlib.patches as patches
+import matplotlib.pyplot as plt
+import numpy as np
+import shutil
+import skimage
+import torch
+import os
+from collections import defaultdict, OrderedDict
+from html4vision import Col, imagetable
+from PIL import Image
+from scipy.ndimage.morphology import distance_transform_edt
+from torch import nn
+from torch.autograd import Variable
+from torchvision.utils import save_image
+from torch.utils.data import Dataset, DataLoader
+
+import util
+import layers
+
+input_size = 128
+output_size = 192
+expand_size = (output_size - input_size) // 2
+patch_w = output_size // 8
+patch_h = output_size // 8
+patch = (1, patch_h, patch_w)
+
+
+# class Generator(nn.Module):
+#     def __init__(self, channels=3, extra_upsample=False):
+#         super(Generator, self).__init__()
+#
+#         def downsample(in_feat, out_feat, normalize=True):
+#             layers = [nn.Conv2d(in_feat, out_feat, 4, stride=2, padding=1)]
+#             if normalize:
+#                 layers.append(nn.BatchNorm2d(out_feat, 0.8))
+#             layers.append(nn.LeakyReLU(0.2))
+#             return layers
+#
+#         def upsample(in_feat, out_feat, normalize=True):
+#             layers = [nn.ConvTranspose2d(in_feat, out_feat, 4, stride=2, padding=1)]
+#             if normalize:
+#                 layers.append(nn.BatchNorm2d(out_feat, 0.8))
+#             layers.append(nn.ReLU())
+#             return layers
+#
+#         if not(extra_upsample):
+#             self.model = nn.Sequential(
+#                 *downsample(channels, 64, normalize=False),
+#                 *downsample(64, 64),
+#                 *downsample(64, 128),
+#                 *downsample(128, 256),
+#                 *downsample(256, 512),
+#                 nn.Conv2d(512, 4000, 1),
+#                 *upsample(4000, 512),
+#                 *upsample(512, 256),
+#                 *upsample(256, 128),
+#                 *upsample(128, 64),
+#                 nn.Conv2d(64, channels, 3, 1, 1),
+#                 nn.Tanh()
+#             )
+#         else:
+#             self.model = nn.Sequential(
[…]

### 2020-05-08 context_residual/train.py

@@ -1,0 +1,99 @@
+import pickle
+import torch
+import torchvision
+from torch import nn, optim
+import matplotlib.pyplot as plt
+
+import local_model
+import outpainting
+
+'''
+Edit the paths here and run to train the GAN.
+Uses GPU:0 with CUDA (feel free to switch to CPU or use DataParallel).
+'''
+
+if __name__ == '__main__':
+    print("PyTorch version: ", torch.__version__)
+    print("Torchvision version: ", torchvision.__version__)
+
+    # Define paths
+    model_save_path = 'outpaint_models'
+    html_save_path = 'outpaint_html'
+    train_dir = '../train'
+    val_dir = '../val'
+    test_dir = '../test'
+
+    # Define datasets & transforms
+    my_tf = torchvision.transforms.Compose([
+            torchvision.transforms.Resize(outpainting.output_size),
+            torchvision.transforms.CenterCrop(outpainting.output_size),
+            torchvision.transforms.RandomHorizontalFlip(),
+            torchvision.transforms.ToTensor()])
+    batch_size = 4
+    train_data = outpainting.CEImageDataset(train_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    val_data = outpainting.CEImageDataset(val_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    test_data = outpainting.CEImageDataset(test_dir, my_tf, outpainting.output_size, outpainting.input_size, outpaint=True)
+    train_loader = outpainting.DataLoader(train_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    val_loader = outpainting.DataLoader(val_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    test_loader = outpainting.DataLoader(test_data, batch_size=batch_size, shuffle=True, num_workers=1)
+    print('train:', len(train_data), 'val:', len(val_data), 'test:', len(test_data))
+
+    # Define model & device
+    device = torch.device('cuda:0')
+    G_net = local_model.CompletionNetwork()
+    CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
+    G_net.apply(outpainting.weights_init_normal)
+    CD_net.apply(outpainting.weights_init_normal)
+    G_net.to(device)
[…]

### 2020-05-09 residual/train.py
added residual multi to train

@@ -5,6 +5,7 @@ from torch import nn, optim
 import matplotlib.pyplot as plt
 
 import outpainting
+import multiple_res_model
 import residual_model
 
 '''
@@ -40,7 +41,7 @@ if __name__ == '__main__':
 
     # Define model & device
     device = torch.device('cuda:0')
-    G_net = residual_model.CompletionNetwork()
+    G_net = multiple_res_model.CompletionNetwork()
     CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
     G_net.apply(outpainting.weights_init_normal)
     CD_net.apply(outpainting.weights_init_normal)

### 2020-05-09 residual/train.py
residual now trains from 10 onwards

@@ -43,16 +43,16 @@ if __name__ == '__main__':
     device = torch.device('cuda:0')
     G_net = multiple_res_model.CompletionNetwork()
     CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
-    G_net.apply(outpainting.weights_init_normal)
-    CD_net.apply(outpainting.weights_init_normal)
+    G_net.load_state_dict(torch.load("outpaint_models/G_9.pt"))
+    CD_net.load_state_dict(torch.load("outpaint_models/D_9.pt"))
     G_net.to(device)
     CD_net.to(device)
     print('device:', device)
 
     # Start training
     data_loaders = {'train': train_loader, 'val': val_loader, 'test': test_loader}  # NOTE: test is evidently not used by the train method
-    n_epochs = 200
-    adv_weight = [0.001, 0.005, 0.015, 0.040]  # corresponds to epochs 1-10, 10-30, 30-60, 60-onwards
+    n_epochs = 50
+    adv_weight = [ 0.005, 0.015, 0.040]  # corresponds to epochs 1-10, 10-30, 30-60, 60-onwards
     hist_loss = outpainting.train(G_net, CD_net, device,
                                   criterion_pxl=nn.L1Loss().to(device),
                                   criterion_D=nn.MSELoss().to(device),

### 2020-05-09 residual/train.py
fixed train for residual

@@ -43,8 +43,8 @@ if __name__ == '__main__':
     device = torch.device('cuda:0')
     G_net = multiple_res_model.CompletionNetwork()
     CD_net = outpainting.ContextDiscriminator((3, outpainting.output_size, outpainting.output_size), (3, outpainting.output_size, outpainting.output_size), arc='places2')
-    G_net.load_state_dict(torch.load("outpaint_models/G_9.pt"))
-    CD_net.load_state_dict(torch.load("outpaint_models/D_9.pt"))
+    G_net.load_state_dict(torch.load("G_9.pt"))
+    CD_net.load_state_dict(torch.load("D_9.pt"))
     G_net.to(device)
     CD_net.to(device)
     print('device:', device)

### 2020-05-10 tex/paper.tex
Added tables to report

@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Title of My Paper}
+\icmltitlerunning{Enhanced Residual Context-based Networks for Image Outpainting}
 
@@
 \twocolumn[
-\icmltitle{Title of My Paper}
+\icmltitle{Enhanced Residual Context-based Networks for Image Outpainting}
 
@@
 \begin{icmlauthorlist}
-\icmlauthor{Aeiau Zzzz}{wpi}
-\icmlauthor{Bauiu C.~Yyyy}{wpi}
+\icmlauthor{Przemek Gardias}{wpi}
+\icmlauthor{Eric Arthur}{wpi}
+\icmlauthor{Huaming Sun}{wpi}
 \end{icmlauthorlist}
@@
 
-\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@wpi.edu}
+\icmlcorrespondingauthor{Przemek Gardias}{pmgardias@wpi.edu}
 
@@
 
+\begin{table}[h] 
+  \centering  
+    \begin{tabular}{c|c|c}  
+    \hline
+    \textbf{layer} & \textbf{output size} & \textbf{parameters}\\ 
+    \hline
+      Conv & 16$\times$192$\times$192 & 5$\times$5, stride=1 \\
+    \hline
+      ResBlock & 128$\times$96$\times$96 & 3$\times$3, stride=2 \\
+    \hline
+      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=2 \\
+    \hline
+      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      ReLU & 256$\times$48$\times$48 & None \\
+    \hline
+      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      ReLU & 256$\times$48$\times$48 & None \\
+    \hline
+      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
+    \hline
+      ReLU & 256$\times$48$\times$48 & None \\
+    \hline
+      Trans-Conv & 128$\times$96$\times$96 & 4$\times$4, stride=1 \\
+    \hline
+      ReLU & 128$\times$96$\times$96 & None \\
+    \hline
+      Conv & 128$\times$96$\times$96 & 3$\times$3, stride=1 \\
+    \hline
+      ReLU & 128$\times$96$\times$96 & None \\
+    \hline
+      Trans-Conv & 64$\times$192$\times$192 & None \\
+    \hline
+      ReLU & 64$\times$192$\times$192 & None \\
+    \hline
+      Conv & 32$\times$192$\times$192 & 3$\times$3, stride=1 \\
+    \hline
+      ReLU & 32$\times$192$\times$192 & None \\
+    \hline
+      Conv & 3$\times$192$\times$192 & 3$\times$3, stride=2 \\
+    \hline
+      Sigmoid & 3$\times$192$\times$192 & None \\
+    \hline
+    \end{tabular}
+
+  \caption{Architecture of generator, including parameters. Trans-Conv is transposed convolution.} 
+  \label{tab:1}
+  \label{table1} 
+\end{table}
+
+\begin{table}[h] 
+  \centering  
+    \begin{tabular}{c|c}  
+    \hline
+    \textbf{layer} & \textbf{parameters}\\ 
+    \hline
+      Conv & 3$\times$3, stride=\(s_{in}\) \\
+    \hline
+      ReLU & None \\
+    \hline
+      Conv & 3$\times$3, stride=\(s_{in}\) \\
+    \hline
+      ReLU & None \\
+    \hline
+      Add & None \\
+    \hline
+    \end{tabular}
+
+  \caption{Architecture of residual block used in generator, including parameters.
+The residual block applies input strides \(s_{in}\) as convolution layer parameters.
+Add is an element-wise addition of \(x_{in}\) and output tensor of previous layer.}
+  \label{tab:2}
+  \label{table2} 
+\end{table}
+
+\begin{table}[h] 
+  \centering  
+    \begin{tabular}{c|c}  
+    \hline
+    \textbf{layer} & \textbf{parameters}\\ 
+    \hline
+      Conv & 3$\times$3, stride=2 \\
+    \hline
+      InstanceNorm & None \\
+    \hline
+      LeakyReLU & negative slope=0.2, inplace=True \\
+    \hline
+      Conv & 3$\times$3, stride=2 \\
+    \hline
+      InstanceNorm & None \\
+    \hline
+      LeakyReLU & negative slope=0.2, inplace=True \\
+    \hline
+      Conv & 3$\times$3, stride=2 \\
+    \hline
+      InstanceNorm & None \\
+    \hline
+      LeakyReLU & negative slope=0.2, inplace=True \\
+    \hline
+      Conv & 3$\times$3, stride=2 \\
+    \hline
+      InstanceNorm & None \\
+    \hline
+      LeakyReLU & negative slope=0.2, inplace=True \\
+    \hline
+      Conv & 3$\times$3, stride=1 \\
+    \hline
+      InstanceNorm & None \\
+    \hline
+      LeakyReLU & negative slope=0.2, inplace=True \\
+    \hline
+      Conv & 3$\times$3, stride=1 \\
+    \hline
+
+    \end{tabular}
+
+  \caption{Architecture of global and local discriminators.} 
+  \label{tab:3}
+  \label{table3} 
+\end{table}
+
 \section{Experiment}

### 2020-05-12 tex/paper.tex
Report update

@@
 \usepackage{subfigure} 
+\usepackage{amsmath}
 
@@
 
-\icmlcorrespondingauthor{Przemek Gardias}{pmgardias@wpi.edu}
+\icmlcorrespondingauthor{}{\{pmgardias, etarthur, hsun2\}@wpi.edu}
 
@@
 % the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{boring formatting information, machine learning, ICML}
+\icmlkeywords{image outpainting, generative adversarial network, context encoder, computer vision, deep learning, machine learning, ICML}
 
@@
     \textbf{layer} & \textbf{output size} & \textbf{parameters}\\ 
-    \hline
+    \hline \hline
       Conv & 16$\times$192$\times$192 & 5$\times$5, stride=1 \\
@@
     \hline
-    \textbf{layer} & \textbf{parameters}\\ 
-    \hline
+    \textbf{Layer} & \textbf{Parameters}\\ 
+    \hline \hline
       Conv & 3$\times$3, stride=\(s_{in}\) \\
@@
     \hline
-    \textbf{layer} & \textbf{parameters}\\ 
-    \hline
+    \textbf{Layer} & \textbf{Parameters}\\ 
+    \hline \hline
       Conv & 3$\times$3, stride=2 \\
@@
 
-  \caption{Architecture of global and local discriminators.} 
+  \caption{Architecture of global and local discriminators $D_G$ and $D_L$, respectively.} 
   \label{tab:3}
@@
 Describe the computational experiments you conducted to validate the approach you took.
+
+Training is done for 50 epochs, with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$, following the same hyperparameters proposed in Van Hoorick 2020 \cite{van_hoorick_image_2020} The loss functions are as follows:
+\begin{align}
+  L_{rec} &= ||x-G(x)||_1 \\
+  L_{adv} &= ||D(G(x))-1||_2^2 \\
+  L_G &= \lambda_{rec}L_{rec} + \lambda_{adv}L_{adv} \\
+  L_D &= ||D(x)-1||_2^2 + ||D(G(x))-0||_2^2
+\end{align}
+
+We apply a time based remedy to the generator loss function that punishes the generator heavier for bad outputs as time progresses.
+
+\begin{align}
+  \lambda_{adv}(n) = \begin{cases}
+    0.001, & \text{if }n\leq10 \\
+    0.005, & \text{if }10<n\leq30 \\
+    0.015, & \text{otherwise}
+  \end{cases}
+  \label{eq:loss_adv}
+\end{align}
+
+Since humans still perform vastly greater than deep learning networks at this task we conclude our experiment with a qualitative discussion about the quality of hallucinations.
+As many previously mentioned models in this domain create noise or lines that are clearly out of place in the hallucinations, we aim to manually evaluate whether our model rectifies this issue or these manifestations are still present.
 
@@
 
-\bibliography{example_paper}
+\bibliography{paper.bib}
 \bibliographystyle{cs541}

### 2020-05-13 tex/paper.tex
Added figs and eqs

@@
 %\usepackage{epsfig} % less modern
-\usepackage{subfigure} 
+\usepackage{subcaption}
 \usepackage{amsmath}
@@
 \begin{abstract} 
-Describe {\bf briefly} the computational problem you tackled, the approach you explored, the analyses you performed, and the results you obtained.
-Point out advantages of your approach compared to prior approaches (if any).
+Although humans perform well at predicting what exists beyond the boundaries of an image, deep models struggle to understand context and extrapolation through retained information.
+This task is known as image outpainting and involves generating realistic expansions of an image’s boundaries.
+Current models use generative adversarial networks to generate results which lack localized image feature consistency and appear fake.
+We propose two methods to improve this issue: the use of a local and global discriminator, and the addition of residual blocks within the encoding section of the network.
+Comparisons of our model and the baseline’s L1 loss, MSE loss, and qualitative differences reveal our model is able to naturally extend object boundaries and produce more internally consistent images compared to current methods but produces lower fidelity images.
 \end{abstract}
@@
 \section{Introduction}
-{\bf Problem before solution}:
-Begin by describing a (computational) {\bf problem} and why the problem is {\bf important}. If previous research has
-explored plausible solutions to solve the problem, then point out how these approaches may be lacking. Then briefly {\bf motivate}
-why a new approach (the approach you explore in this paper) is worth exploring. Don't go into too much detail yet how it works -- that will
-be left for Section \ref{sec:proposed_method}).
+The use of generative adversarial models has led to many new developments in the computer vision field.
+The task known as image inpainting, which aims to enhance or restore quality to parts of an image, requires a model to retain the context of the image while completing missing regions of the image, and iteratively improve the process of the generations.
+The problem explored in this paper is a significantly more ambiguous task than its inpainting alternative, and is commonly known as image outpainting.
+For this task, the input image boundaries are extrapolated outside of the original content of the input based upon the context of the image.\cite{sabini_painting_2018}
+
+\begin{figure}
+	\captionsetup[subfigure]{labelformat=empty}
+    \centering
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig1/masked_input}
+        \caption{Masked input}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig1/baseline}
+        \caption{Output}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig1/ground_truth}
+        \caption{GT}
+    \end{subfigure}
+  	\caption{Example of image outpainting.}
+  	\label{fig:fig1}
+\end{figure}
+
+Image outpainting, sometimes referred to as image context interpretation and extrapolation, requires the context of the image to be retained by the encoder to accurately re-generate the known input image, then create new portions to append to the edges of the image as shown in Figure \ref{fig:fig1}.
+There exists research on this task using GANs, however one of the biggest issues with image outpainting is the new additions to the image, known as hallucinations, typically appear lower quality than the base image and therefore can easily be distinguished as fake by the human eye.\cite{sabini_painting_2018} Therefore, to effectively create higher quality hallucinations, better image evaluation methods are required to match the discrimination abilities of human interpretation.
 
 \subsection{Research contributions}
-Describe clearly and concisely what your paper {\bf uniquely} contributes to the research community, i.e., that has never been done before.
+We provide insight into the use of a local discriminator alongside a global discriminator to improve the quality of hallucinations, additionally evaluating the performance of residual blocks applied to the context encoder portion of our generative network.
 
 \section{Related Work}
-Describe previous approaches (in somewhat greater detail than the introduction) to tackling the problem. Pick any citation style you prefer and use it
-consistently (here's a random citation \cite{mitchell80}). Explain how previous work may be lacking in certain ways, and use your critical review
-of prior work to further motivate your research.
+In this section, we briefly review the previous works relating to this paper in three sub-fields: Generative Adversarial Networks, Image Inpainting, and Image Outpainting.
+
+\subsection{Generative Adversarial Networks}
+Deep generative models have shown success in various tasks of image and video generation problems.
+By training the generator and discriminator in tandem, the generator can capture the real data distribution and create more realistic images given the latent input.
+However, GANs are often prone to collapse and are difficult to train.
+Therefore, some newer techniques have been applied attempting to reduce this issue such as the addition of residual blocks to the encoder component of the generator specifically researched within a super-resolution task context.\cite{lim_enhanced_2017}
+
+\subsection{Image Inpainting}
+Image inpainting is the task of recovering missing regions or enhancing regions within images.
+Pathak et al.
+demonstrate that context encoder can achieve realistic results for generation of novel images sections for inpainting purposes.\cite{pathak_context_2016} Recent improvements include applying global and local discriminators to improve the generated feature consistency within the missing sections of the input image by identifying poor generations only within the area of the inpainted sections.\cite{iizuka_globally_2017} Liu et al.
+more recently apply partial convolutions to improve overall consistency of generated images.\cite{liu_image_2018}
 
 \section{Proposed Method}
-\label{sec:proposed_method}
-Describe the computational approach -- based obviously on neural networks -- that you took to tackle the problem.
+In this section, we provide an overview of our architecture.
+Since the task is generative we use a GAN which other current methods employ.
+Our GAN is based on the architecture provided by Van Hoorick with two major additions: the first being the use of residual blocks in the generator, and the second being the use of two discriminators.\citep{van_hoorick_image_2020} Below we explore the exact architecture and some design decisions behind it.
+
+\subsection{Generator}
+We propose a GAN architecture that aims to encode the context of the image and use deconvolutional layers to then generate the resulting image while retaining feature consistency.
+We apply a residual model to the generative network, first convolving the image down into its feature space, then using deconvolution to upsample the image into its expanded version.
+Although typical models that contain residual blocks often include batch normalization within the blocks, we do not include this activation layer per demonstrations of improvement in the deblurring work of Nah et al.\cite{nah_deep_2018} The encoder section of the generative network contains multiple residual blocks in an attempt to improve image quality.
+Table \ref{tab:1} outlines the layers of our generative network, including both the encoder and decoder components.
 
@@
   \centering  
-    \begin{tabular}{c|c|c}  
+    \begin{tabular}{lcc}  
     \hline
@@
 
-  \caption{Architecture of generator, including parameters. Trans-Conv is transposed convolution.} 
+  \caption{Architecture of generator $G$, including parameters. Trans-Conv is transposed convolution.} 
   \label{tab:1} 
-  \label{table1} 
 \end{table}
@@
   \centering  
-    \begin{tabular}{c|c}  
+    \begin{tabular}{lc}  
     \hline
@@
     \hline \hline
-      Conv & 3$\times$3, stride=\(s_{in}\) \\
+      Conv & 3$\times$3, stride=$s_{in}$ \\
     \hline
@@
     \hline
-      Conv & 3$\times$3, stride=\(s_{in}\) \\
+      Conv & 3$\times$3, stride=$s_{in}$ \\
     \hline
@@
 
-  \caption{Architecture of residual block used in generator, including parameters.
-The residual block applies input strides \(s_{in}\) as convolution layer parameters.
-Add is an element-wise addition of \(x_{in}\) and output tensor of previous layer.}
+  \caption{Architecture of residual block used in generator $G$, including parameters.
+The residual block applies input strides $s_{in}$ to the convolution layer.
+Add is an element-wise addition of block input tensor $x$ and output tensor of previous layer.}
   \label{tab:2}
-  \label{table2} 
 \end{table}
+
+\subsection{Discriminator}
+Our discriminator network $D$ consists of dual discriminators.
+One discriminator $D_G$ takes as input the entire generated image and applies a convolutional network to identify the image as real or generated, while the second discriminator $D_L$ is local, and is restricted solely to the boundaries between the input image and the hallucinations.
+These discriminator outputs are averaged, meaning our total discriminator network output is
+
+\begin{align}
+	D(x) &= \frac{D_L(\mu \times x) + D_G(x)}{2}
+\end{align}
+
+where $\mu$ is the binary mask which is originally applied to the training images.
+
+The purpose of the local discriminator is to attempt to remove the clearly fake hallucinations that result from pixel noise or manifestations, that to the human eye are clearly fake.
+Since these happen in the boundary between the input image and the hallucinations, the local discriminator focuses on these areas alone as shown in Table \ref{tab:3}.
 
@@
     \hline
-      LeakyReLU & negative slope=0.2, inplace=True \\
+      LeakyReLU & negative slope=0.2 \\
     \hline
@@
     \hline
-
     \end{tabular}
@@
   \label{tab:3}
-  \label{table3} 
 \end{table}
@@
 Training is done for 50 epochs, with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$, following the same hyperparameters proposed in Van Hoorick 2020 \cite{van_hoorick_image_2020} The loss functions are as follows:
+
 \begin{align}
@@
   \end{cases}
-  \label{eq:loss_adv}
 \end{align}
@@
 \section{Results}
-Describe the results of the experiments, including their immediate implications (e.g., ``the result suggests that technique A performs better
-than technique B''). If your work is purely theoretical, then this section (as well as the previous section) might be replaced with mathematical proofs.
+Describe the results of the experiments, including their immediate implications (e.g., ``the result suggests that technique A performs better than technique B'').
+If your work is purely theoretical, then this section (as well as the previous section) might be replaced with mathematical proofs.
+
+\begin{table}[h] 
+  \centering  
+    \begin{tabular}{lrrr}
+    \hline
+    \textbf{Model} & \textbf{L1} & \textbf{MSE} & \textbf{Adversarial}\\ 
+    \hline \hline
+      Baseline & $0.0956$ & $0.047$ & $0.1278$ \\
+      Local Discriminator & $0.897$ & $1.044$ & $0.1014$ \\
+      Residual Encoder & $0.08$ & $0.7814$ & $0.0941$ \\
+    \hline
+    \end{tabular}
+
+  \caption{TODO} 
+  \label{tab:4}
+\end{table}
+
+\begin{figure*}
+	\captionsetup[subfigure]{labelformat=empty}
+    \centering
+    \begin{subfigure}[b]{0.175\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig2/masked_input}
+        \caption{Masked input}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.175\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig2/baseline}
+        \caption{Baseline}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.175\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig2/local}
+        \caption{Discriminator}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.175\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig2/residual}
+        \caption{Residual}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.175\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig2/ground_truth}
+        \caption{GT}
+    \end{subfigure}
+  	\caption{Comparison of results for different model variants.}
+  	\label{fig:fig2}
+\end{figure*}
+
+\begin{figure}
+	\captionsetup[subfigure]{labelformat=empty}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig3/fig3}
+        \caption{
+        	\begin{tabular}{ccc}
+        	Masked input & Local & GT
+        	\end{tabular}
+        }
+    \end{subfigure}
+  	\caption{Outpainting example using local discriminator model.}
+  	\label{fig:fig3}
+\end{figure}
+
+\begin{figure}
+	\captionsetup[subfigure]{labelformat=empty}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig4/fig4}
+    \end{subfigure}
+  	\caption{Outpainting result example using residual encoder model.}
+  	\label{fig:fig4}
+\end{figure}
+
+\begin{figure}
+	\captionsetup[subfigure]{labelformat=empty}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig5/fig5}
+    \end{subfigure}
+  	\caption{Example of anomaly with the hallucination.}
+  	\label{fig:fig5}
+\end{figure}
 

### 2020-05-13 tex/paper.tex
Finalized report and figures

@@
 \usepackage{times}
+
 % For figures
@@
 
+\usepackage{enumitem}
+
 % For citations
-\usepackage{natbib}
+\usepackage[sort&compress,numbers,square,comma,authoryear]{natbib}
 
@@
 \usepackage[accepted]{cs541}
+\setcitestyle{sort&compress,numbers,square,comma}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Enhanced Residual Context-based Networks for Image Outpainting}
+\icmltitlerunning{Enhanced Residual Networks for Context-based Image Outpainting}
 
@@
 \twocolumn[
-\icmltitle{Enhanced Residual Context-based Networks for Image Outpainting}
+\icmltitle{Enhanced Residual Networks for Context-based Image Outpainting}
 
@@
 We propose two methods to improve this issue: the use of a local and global discriminator, and the addition of residual blocks within the encoding section of the network.
-Comparisons of our model and the baseline’s L1 loss, MSE loss, and qualitative differences reveal our model is able to naturally extend object boundaries and produce more internally consistent images compared to current methods but produces lower fidelity images.
+Comparisons of our model and the baseline’s L1 loss, mean squared error (MSE) loss, and qualitative differences reveal our model is able to naturally extend object boundaries and produce more internally consistent images compared to current methods but produces lower fidelity images.\footnote[2]{A repository containing relevant source code, and accompanying instructions, is accessible via \href{https://github.com/etarthur/Outpainting}{GitHub}.}
 \end{abstract}
@@
 The problem explored in this paper is a significantly more ambiguous task than its inpainting alternative, and is commonly known as image outpainting.
-For this task, the input image boundaries are extrapolated outside of the original content of the input based upon the context of the image.\cite{sabini_painting_2018}
+For this task, the input image boundaries are extrapolated outside of the original content of the input based upon the context of the image \citep{sabini_painting_2018}.
 
@@
 Image outpainting, sometimes referred to as image context interpretation and extrapolation, requires the context of the image to be retained by the encoder to accurately re-generate the known input image, then create new portions to append to the edges of the image as shown in Figure \ref{fig:fig1}.
-There exists research on this task using GANs, however one of the biggest issues with image outpainting is the new additions to the image, known as hallucinations, typically appear lower quality than the base image and therefore can easily be distinguished as fake by the human eye.\cite{sabini_painting_2018} Therefore, to effectively create higher quality hallucinations, better image evaluation methods are required to match the discrimination abilities of human interpretation.
+There exists research on this task using generative adversarial networks, however one of the biggest issues with image outpainting is the new additions to the image, known as hallucinations, typically appear lower quality than the base image and therefore can easily be distinguished as fake by the human eye \citep{sabini_painting_2018}.
+Therefore, to effectively create higher quality hallucinations, better image evaluation methods are required to match the discrimination abilities of human interpretation.
 
 \subsection{Research contributions}
-We provide insight into the use of a local discriminator alongside a global discriminator to improve the quality of hallucinations, additionally evaluating the performance of residual blocks applied to the context encoder portion of our generative network.
+We provide insight into the use of a local discriminator alongside a global discriminator to improve the quality of hallucinations.
+Specifically, we analyze how dual discriminators assist in smoothing the sudden change in quality between hallucinations and original image.
+Additionally, we successfully implement residual blocks applied to the context encoder portion of our generative network to improve the quality of images.
+We evaluate the performance of these two networks by comparing to the baseline model provided by Van Hoorick using a time based remedy to the generator loss function \citep{van_hoorick_image_2020}.
 
@@
 However, GANs are often prone to collapse and are difficult to train.
-Therefore, some newer techniques have been applied attempting to reduce this issue such as the addition of residual blocks to the encoder component of the generator specifically researched within a super-resolution task context.\cite{lim_enhanced_2017}
+Therefore, some newer techniques have been applied attempting to reduce this issue such as the addition of residual blocks to the encoder component of the generator specifically researched within a super-resolution task context \citep{lim_enhanced_2017}.
 
@@
 Pathak et al.
-demonstrate that context encoder can achieve realistic results for generation of novel images sections for inpainting purposes.\cite{pathak_context_2016} Recent improvements include applying global and local discriminators to improve the generated feature consistency within the missing sections of the input image by identifying poor generations only within the area of the inpainted sections.\cite{iizuka_globally_2017} Liu et al.
-more recently apply partial convolutions to improve overall consistency of generated images.\cite{liu_image_2018}
+demonstrate that context encoder can achieve realistic results for generation of novel images sections for inpainting purposes \citep{pathak_context_2016}.
+Recent improvements include a local discriminator to improve the generated feature consistency within the missing sections of the input image by identifying poor generations only within the area of the inpainted sections \citep{iizuka_globally_2017}.
+More recently, Liu et al.
+apply partial convolutions to improve overall consistency of generated images \citep{liu_image_2018}.
+
+\subsection{Image Outpaint}
+Image outpainting refers to predicting the region beyond the borders of an image.
+Compared to image inpainting, it has been significantly less studied.
+Although there are promising works on this problem, they include limitations such as application to very specific domain datasets or result in low quality of hallucinations \citep{van_hoorick_image_2020}\citep{wang_wide-context_2019}.
+More recent work utilizes a deep neural network with both global and local discriminator, recurrent content transfer, skip horizontal connection, and a global residual block to achieve impressive results \citep{yang_very_2019}.
+However, this approach focuses  on recursive horizontal hallucinations on a natural scenes dataset, resulting in a network which prioritizes clearly defined horizontal lines often found in landscape images.
 
@@
 In this section, we provide an overview of our architecture.
-Since the task is generative we use a GAN which other current methods employ.
-Our GAN is based on the architecture provided by Van Hoorick with two major additions: the first being the use of residual blocks in the generator, and the second being the use of two discriminators.\citep{van_hoorick_image_2020} Below we explore the exact architecture and some design decisions behind it.
-
-\subsection{Generator}
-We propose a GAN architecture that aims to encode the context of the image and use deconvolutional layers to then generate the resulting image while retaining feature consistency.
-We apply a residual model to the generative network, first convolving the image down into its feature space, then using deconvolution to upsample the image into its expanded version.
-Although typical models that contain residual blocks often include batch normalization within the blocks, we do not include this activation layer per demonstrations of improvement in the deblurring work of Nah et al.\cite{nah_deep_2018} The encoder section of the generative network contains multiple residual blocks in an attempt to improve image quality.
-Table \ref{tab:1} outlines the layers of our generative network, including both the encoder and decoder components.
+Since the task is generative we use a GAN in a similar context-encoding method compared to current methods \citep{van_hoorick_image_2020}\citep{pathak_context_2016}.
+Our GAN architecture contains two major additions: the first being the use of residual blocks in the generator, and the second being the use of two discriminators.
+Below, we explore our architecture choices and some design decisions behind it.
 
@@
 
+\subsection{Generator}
+We propose a GAN architecture that aims to encode the context of the image and use deconvolutional layers to then generate the resulting image while retaining feature consistency.
+We apply a residual model to the generative network, first convolving the image down into its feature space, then using deconvolution to upsample the image into its expanded version.
+Although typical models that contain residual blocks often include batch normalization within the blocks, we do not include this activation layer per demonstrations of improvement in the deblurring work of Nah et al \citep{nah_deep_2018}.
+The encoder section of the generative network contains multiple residual blocks in an attempt to improve image quality.
+Table \ref{tab:1} outlines the layers of our generative network, including both the encoder and decoder components.
+Table \ref{tab:2} showcases the individual layers which are used to construct a residual block.
+
 \subsection{Discriminator}
@@
 One discriminator $D_G$ takes as input the entire generated image and applies a convolutional network to identify the image as real or generated, while the second discriminator $D_L$ is local, and is restricted solely to the boundaries between the input image and the hallucinations.
-These discriminator outputs are averaged, meaning our total discriminator network output is
-
+These discriminator outputs are averaged as such, where $\epsilon$ represents the binary mask which is originally applied to the training images:
 \begin{align}
-	D(x) &= \frac{D_L(\mu \times x) + D_G(x)}{2}
+	D(x) &= \frac{D_L(\epsilon \times x) + D_G(x)}{2}
 \end{align}
 
-where $\mu$ is the binary mask which is originally applied to the training images.
-
-The purpose of the local discriminator is to attempt to remove the clearly fake hallucinations that result from pixel noise or manifestations, that to the human eye are clearly fake.
-Since these happen in the boundary between the input image and the hallucinations, the local discriminator focuses on these areas alone as shown in Table \ref{tab:3}.
+The purpose of the local discriminator is to attempt to remove the clearly fake hallucinations that result from low-quality generations or manifestations, which immediately appear fake to the human eye.
+Since these happen in the boundary between the input image and the hallucinations, the local discriminator focuses on the hallucination alone.
 
@@
 
-\section{Experiment}
-Describe the computational experiments you conducted to validate the approach you took.
-
-Training is done for 50 epochs, with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$, following the same hyperparameters proposed in Van Hoorick 2020 \cite{van_hoorick_image_2020} The loss functions are as follows:
-
-\begin{align}
-  L_{rec} &= ||x-G(x)||_1 \\
-  L_{adv} &= ||D(G(x))-1||_2^2 \\
-  L_G &= \lambda_{rec}L_{rec} + \lambda_{adv}L_{adv} \\
-  L_D &= ||D(x)-1||_2^2 + ||D(G(x))-0||_2^2
-\end{align}
-
-We apply a time based remedy to the generator loss function that punishes the generator heavier for bad outputs as time progresses.
-
-\begin{align}
-  \lambda_{adv}(n) = \begin{cases}
-    0.001, & \text{if }n\leq10 \\
-    0.005, & \text{if }10<n\leq30 \\
-    0.015, & \text{otherwise}
-  \end{cases}
-\end{align}
-
-Since humans still perform vastly greater than deep learning networks at this task we conclude our experiment with a qualitative discussion about the quality of hallucinations.
-As many previously mentioned models in this domain create noise or lines that are clearly out of place in the hallucinations, we aim to manually evaluate whether our model rectifies this issue or these manifestations are still present.
-
-\section{Results}
-Describe the results of the experiments, including their immediate implications (e.g., ``the result suggests that technique A performs better than technique B'').
-If your work is purely theoretical, then this section (as well as the previous section) might be replaced with mathematical proofs.
-
-\begin{table}[h] 
-  \centering  
-    \begin{tabular}{lrrr}
-    \hline
-    \textbf{Model} & \textbf{L1} & \textbf{MSE} & \textbf{Adversarial}\\ 
-    \hline \hline
-      Baseline & $0.0956$ & $0.047$ & $0.1278$ \\
-      Local Discriminator & $0.897$ & $1.044$ & $0.1014$ \\
-      Residual Encoder & $0.08$ & $0.7814$ & $0.0941$ \\
-    \hline
-    \end{tabular}
-
-  \caption{TODO} 
-  \label{tab:4}
-\end{table}
-
 \begin{figure*}
@@
         \includegraphics[width=\textwidth]{figs/fig2/local}
-        \caption{Discriminator}
+        \caption{Local}
     \end{subfigure}
@@
     \end{subfigure}
-  	\caption{Comparison of results for different model variants.}
+  	\caption{Comparison of results for different models. Note the baseline result appears larger but contains the same ratio of hallucination to input pixels as the other generated images.}
   	\label{fig:fig2}
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figs/fig3/fig3}
-        \caption{
-        	\begin{tabular}{ccc}
-        	Masked input & Local & GT
-        	\end{tabular}
-        }
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig3/masked_input}
+        \caption{Masked input}
     \end{subfigure}
-  	\caption{Outpainting example using local discriminator model.}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig3/local}
+        \caption{Local}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{figs/fig3/ground_truth}
+        \caption{GT}
+    \end{subfigure}
+  	\caption{Outpainting example of the local discriminator model.}
   	\label{fig:fig3}
 \end{figure}
+
+\section{Experiment}
+To evaluate the effectiveness of our model we compare MSE and L1 loss between each of our models.
+Furthermore, we qualitatively analyze the outputs from our models due to the inherently visual nature of this problem.
+
+We use MIT CSAIL Places365-Standard, a large scale scene dataset used to train models for image context and recognition \citep{zhou_places_2017}.
+This dataset contains around 2 million images, combined, of random scenes from outdoor and indoor scenery, including both simple landscapes and detailed, object-heavy images.
+We use this dataset as our primary method of evaluation because of its usage in Van Hoorick \citep{van_hoorick_image_2020}.
+Therefore, a direct comparison of MSE loss is more meaningful.
+Unfortunately, due to computing time constraints, training on the whole of the dataset was deemed implausible, therefore we drastically reduced the size of the training set to approximately 25,000 images and trained for 50 epochs.
+The size of the validation set was reduced to be relatively proportional to the training set decrease.
+During this process, we kept images which were chosen randomly from the full dataset, a process which adds some inherent weaknesses to the training of our model.
+To take into consideration these limitations, we trained three models:
+\begin{itemize}
+\setlength{\partopsep}{0pt}
+\setlength{\topsep}{0pt}
+\setlength{\itemsep}{0pt}
+	\item{The model proposed by Van Hoorick, which is herein referred to as ``baseline''.}
+	\item{A model which adds on a local discriminator to the existing context encoder architecture, averaging the results of the dual discriminators. This model is herein referred to as ``local''.}
+	\item{A model which uses residual blocks as part of the context encoder network, as well as includes the dual discriminators. This model is herein referred to as ``residual''.}
+\end{itemize}
+To address the weakness which training on a subset of the dataset introduce, we train the baseline model on the same training set which is used for the latter two models.
+
+We trained each of our models with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$, following the same training considerations proposed by Van Hoorick \citep{van_hoorick_image_2020}.
+The loss functions are as follows:
+\begin{align}
+  L_{rec} &= ||x-G(x)||_1 \\
+  L_{adv} &= ||D(G(x))-1||_2^2 \\
+  L_G &= \lambda_{rec}L_{rec} + \lambda_{adv}L_{adv} \\
+  L_D &= ||D(x)-1||_2^2 + ||D(G(x))-0||_2^2
+\end{align}
+We apply a time based remedy to the generator loss function that punishes the generator heavier for bad outputs as time progresses:
+\begin{align}
+  \lambda_{adv}(n) = \begin{cases}
+    0.001, & \text{if }n\leq10 \\
+    0.005, & \text{if }10<n\leq30 \\
+    0.015, & \text{otherwise}
+  \end{cases}
+\end{align}
+Since humans still perform vastly greater than deep learning networks at this task we conclude our experiment with a qualitative discussion about the quality of hallucinations.
+As many previously mentioned models in this domain create noise or extrapolations in the hallucinations that clearly appear faulty, we aim to manually evaluate whether our model rectifies this issue or these manifestations are still present.
+
+\section{Results}
+We first provide a comparison of the losses for each model in Table \ref{tab:4} that demonstrates the residual model performs marginally better with respect to L1 and adversarial loss.
+However, as a comparison of the loss values does not cover all of the results in detail, we provide a further discussion of the qualitative results, which provides insights to the strengths and weakness of our approaches.
+
+\begin{table}[h] 
+  \centering  
+    \begin{tabular}{lrrr}
+    \hline
+    \textbf{Model} & \textbf{L1} & \textbf{MSE} & \textbf{Adversarial}\\ 
+    \hline \hline
+      Baseline & $0.0956$ & $0.047$ & $0.1278$ \\
+      Local Discriminator & $0.897$ & $1.044$ & $0.1014$ \\
+      Residual Encoder & $0.08$ & $0.7814$ & $0.0941$ \\
+    \hline
+    \end{tabular}
+
+  \caption{Comparison of all loss results across each of the models.} 
+  \label{tab:4}
+\end{table}
+
+The baseline model performs better at directly reconstructing the images compared to their ground truths, as demonstrated by the significantly lower MSE, however the local discriminator and residual models result in an L1 loss which is marginally lower than the baseline model's L1 loss.
+Since we set out not to improve the reconstruction but rather the quality of the reconstructed image, the change in MSE is expected.
+Finally,  moderately lower adversarial loss of the local and residual models reflects our goal with the implementation of dual discriminators, demonstrating their strength in determining fake generated images.
+
+We aim to create a model that generates cleaner or higher quality hallucinations such that it is not evident to the human eye if it is fake or real.
+Per Figure \ref{fig:fig2}, we can demonstrate our approach is able to achieved a clearer continuous output.
+As shown below the second image is the output from the baseline model, and it is quite evident where the original image ends and the new hallucinations appear.
+Compared to the output from our local discriminator model, it is much harder to tell where the original image ends and the hallucinations appear.
+This is because our model is able to effectively continue object boundaries into the hallucinations which the baseline cannot.
+A side effect of this is that the whole image becomes blurrier which explains the increase in MSE, however qualitatively we believe the outputs show that our local discriminator model does a significantly better job at creating continuous realistic hallucinations compared to the baseline as we set out to achieve.
+Finally, our residual blocks model appears to revert the beneficial qualities of having two discriminators as shown by the obvious boundaries in the fourth image of figure \ref{fig:fig2}.
+The residual blocks allowed for the input image to remain high quality, but the use of a local discriminator lowered the quality of the hallucinations resulting in a model very close in effectiveness to the baseline.
 
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \includegraphics[width=\textwidth]{figs/fig4/fig4}
     \end{subfigure}
-  	\caption{Outpainting result example using residual encoder model.}
+  	\caption{Outpainting result example for the residual encoder model.}
   	\label{fig:fig4}
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \includegraphics[width=\textwidth]{figs/fig5/fig5}
     \end{subfigure}
-  	\caption{Example of anomaly with the hallucination.}
+  	\caption{Example of an anomaly with the hallucination, generated during the training process.}
   	\label{fig:fig5}
@@
 
+With further examination we can report that the local discriminator model may reduce the quality of the input image, but by doing so can create more realistic outputs as shown in Figure \ref{fig:fig3}.
+The detail in the original image is not prioritized to be preserved but instead the overall continuity of the image is.
+For example, the individual peaks atop the structure are lost but the new generations match the quality of the blurred input image.
+Furthermore, it is evident that our model is able to effectively continue object boundaries into the hallucinations.
+Comparatively, the baseline model struggles to do this, and therefore our model provides a large improvement in this regard.
+Because of this the output image looks quite believable as there is internal consistency within the image that is lost in the baseline model.
+
+Next, our residual blocks model which contains both a local and discriminator seemed to revert some of the benefits of having both discriminators.
+As shown in Figure \ref{fig:fig4}, the residual blocks model allowed for the input image to remain high quality but since it uses the local discriminator the hallucinations are of reduced quality.
+These two effects combined creates a clearly fake output image where the boundary of the original input image is clearly defined.
+The output appears marginally better than the baseline, however the hallucinations remain lower quality even though the entirety of the image is of higher quality than the local discriminator model's results.
+
+Finally, due to the inclusion of the local discriminator our models place a significant emphasis on the hallucinations.
+This, combined with the fact that we do not use batch normalization, increases the likelihood of erroneous anomalies, as is exemplified in Figure \ref{fig:fig5}.
+Since our model attempts to blur the boundary zones between the base image and the hallucinations the anomaly is stretched and warped across the image.
+
 \section{Discussion}
-Describe limitations of your work as well as further-ranging implications (e.g., ``our work suggests that doing XYZ in general may be a useful approach to...'').
+A major limitation of our experiment was the size of the training set and number of epochs we were able to fit in our limited computing time.
+Using just 200,000 images from the  Places365 dataset on the single NVIDIA Tesla P4 we used for training would have taken approximately a week for 200 epochs.
+Therefore, we reduced the dataset down to approximately 25,000 images randomly.
+The effects of this blind reduction of training data resulted in our models struggling to learn complex features such as humans and water details.
+This problem is even more compounded since humans were included in only a small subset of the images we used.
+This limitation could have been overcome with more time or better computational capabilities to train on a larger dataset.
+Alternatively, a smaller dataset could be used which requires significantly less information to be contained within the latent space.
+Furthermore, our reduced dataset could have been manually picked to only include images of landscapes to focus on one specific image type, albeit this approach would take an unreasonably excessive amount of tedious effort to properly
+
+Another limitation to our approach is that our models use a fixed average between the global and local discriminator.
+Therefore, it weighs the overall image and the boundary areas equally.
+This issues relates to the creation of anomalies, as shown in \ref{fig:fig5}, and why the images appear blurrier or lower quality overall.
+The easiest way to rectify this would be to include a method of back-propagate the error to the discriminator-combining weight and allow the models to learn how to combine the discriminator outputs.
+The models would then hopefully be able to balance higher quality images and consistency whereas our discussed approach focuses exclusively on consistency.
+
+Since the MSE loss in this task is the measure of how well the models can reconstruct the ground truth image it may not have been an appropriate measurement for our specific problem of increasing the hallucination boundary quality of the images.
+Since our local discriminator and global discriminator have separate goals the MSE loss of our models was ultimately higher than the baseline.
+Therefore, the quantitative measure of MSE loss fails to reveal how our models excel.
+Unfortunately, we were unable to find another loss function for image consistency and retrain in time to publish these results.
+%Our models also offers some insight and ramifications as how to improve output image quality.
+The largest contribution our models provides is the ability to generate higher quality and more internally consistent output images.
+This was done through the use of both a local and global discriminator.
+This technique effectively allows for the model to continue object boundaries into the hallucinations which prior models cannot.
+This comes with the downside of having an overall lower quality output, which could be rectified as described prior.
+Overall, we believe the downsides can be solved using other techniques such as having the model learn the weighted average between the discriminators and therefore more research should be on using both a local and global discriminator to improve output image quality.
+
+Finally, the residual blocks model demonstrate increased image fidelity of the original input image inside of the hallucinations.
+Adding the residual blocks to the local discriminator model seems to ``revert'' the focus of the generator closer to the baseline, as the boundary regions become more defined.
+Therefore, we recommend further experimentation into the usage of residual blocks as part of the encoding network, including using residual blocks after the generation as a post-processing technique to construct higher quality output images.
 
 \section{Conclusions and Future Work}
-Briefly summarize the key findings your paper and point out interesting directions for future inquiry.
+Image outpainting is an attractive task that currently suffers from low quality or obviously fake outputs.
+The models we created show that the use of a local and global discriminator allows for higher consistency within the output images and object boundaries may be continued into the newly generated areas.
+This is an improvement over other models and shows promise into ways to improve output quality.
+Further research is needed to improve the fidelity of these outputs, however the consistency of these images makes it significantly harder to detect fake outputs compared to other models.
 
-\bibliography{paper.bib}
-\bibliographystyle{cs541}
+Obvious improvements may be conducted related to the architecture and training of our models. Below we identify possible future work to extend our contribution to the problem:
+\begin{itemize}
+\setlength{\partopsep}{0pt}
+\setlength{\topsep}{0pt}
+\setlength{\itemsep}{1pt}
+	\item{Comprehensive training on the entire two million image dataset for an increased number of epochs will yield significantly cleaner and robust results.}
+	\item{The use of a local and global discriminator greatly improves object boundaries but dampens the overall quality of the image.
+This may be rectified by allowing the model to learn a combining weight for the combination of the dual discriminators using back-propagation.}
+	\item{A more appropriate loss function to reinforce feature consistency across the boundary of the input image and the hallucination.
+For example, a loss function which rewards finer generated object boundaries, possibly even drawing from traditional computer vision techniques for feature detection across the ground truth and outpainting result.}
+\end{itemize}
+
+\bibliographystyle{unsrt}
+\bibliography{paper}
 
